---
title: "labvsfield_QMRA"
author: "Camille Zimmer"
date: "2024-03-01"
output: html_document
---

```{r setup, include=FALSE, set.seed(123)}
knitr::opts_chunk$set(echo = TRUE)

#Clear environment
rm(list = ls())

#Load libraries
library(tidyverse)       # For tidy datasets and graphing 
library(fitdistrplus)    # For fitting distributions
library(readxl)          # For reading excel files
library(writexl)         # For writing excel files
library(mc2d)            # For monte carlo draws
library(truncnorm)       # To draw from a truncated normal distribution
library(patchwork)       # For graphing, to stitch multiple graphs together
library(RColorBrewer)    # For making nicely coloured graphs
library(gt)              # For making summary tables

# Define number of Monte Carlo observations we want per draw (currently 100 for the first chunks, will be redefined further down)
nMC = 100

```


```{r load field LRV data, include=FALSE}

## Load in spreadsheet of LRVs from fieldwork, with corresponding manufacturer claims if available
# This df is used below in the chunk "cycle through all the manuf-field LRV pairs"
rawLRVdata = read_excel("inputdata/LRVs_forQMRA.xlsx", skip = 5)

## Data wrangling
# Select relevant columns and drop rows with no manufacturer claim
rawLRVdata = rawLRVdata %>%
    dplyr::select(row_num, 
                  treatment_type,
                  treatment_name,
                  organism,
                  LRV_field,
                  LRV_manuf
                  ) %>%
    drop_na()

```


# Part I:  define MC draw functions for QMRA 
## Draw for pathogen concentration in the raw water, for each "DW event"
### Draw for campylobacter
```{r draw_campy}

# See "fitenvdata_forQMRAinputs" file for code used to find fit parameters

# Function inputs:
#  nMC: the number of monte carlo draws to carry out
#  plotsdisp: whether to display a summary plot of one of the refill draws
#  Distribution parameters (prevalence and concentration) are initialized within the function

# Function outputs:
#  rawcampyconc: a 21 x nMC dataframe where each column is nMC draws for campylobacter concentration for a given water refill
#  Note: rawcampyconc has units of CFU/L
draw_campy = function(nMC, plotsdisp) {
    
        # See "fitenvdata_forQMRAinputs" code for code and data used to find fit parameters
        # We'll use meanlog = 1.94, sdlog = 2.22 (Units in CFU/100 mL) --> per Pintar et al (2017)
        
        list = list() #create an empty list
        
        # First, draw nMC times for the campy concentration
                for (i in 1:21) {
                    vec = numeric(nMC) #preallocate a numeric vector
                    vec = rlnorm(nMC, meanlog = 1.94, sdlog = 2.22) # Units in CFU/100 mL
                    list[[i]]  = vec
                }
        
        # Wrangle data
        rawcampyconc = do.call("rbind",list)
        rawcampyconc = as.data.frame(rawcampyconc)
        rawcampyconc = t(sapply(rawcampyconc, as.numeric))
        rawcampyconc = as.data.frame(rawcampyconc)


        # Replace some % of values with non-detect to account for prevalence
        # Prevalence taken from Murphy et al (2016), which is a PERT dist with min = 0, mode = 0.25, max = 0.587 (shape factor not specified)
        # https://stackoverflow.com/questions/70401107/r-randomly-changing-values-in-a-dataframe
        # https://stackoverflow.com/questions/72313629/r-randomly-replace-values-with-na
        # In cases where values are replaced with zero, instead replace them with a value from a PDF to reflect the LDL of Campy sampling
        # For campy, the LDL is 1 CFU/100 mL, so 10 CFU in 1 L.  
        # Make function to replace some % of values with a non-detect
            FUNcampy = function(x) {
                censvaluecampy = runif(1, min = 0, max = 1) # Units in CFU/100 mL, define the non-detect value
                probcampy = rpert(1, min = 0, mode = 0.25, max = 0.578) # probability of a non-detect
                sample(c(x, censvaluecampy), 1, prob=c(probcampy,(1 - probcampy))) # Replace values in the rawcampyconc df with non-detects
                }
        rawcampyconc <- as.data.frame(apply(rawcampyconc, 1:2, FUNcampy)) # Use FUNcampy function to replace values; units in CFU/100 mL
        rawcampyconc = rawcampyconc * 10 # Get in units of CFU/1 L

        #Visualise one of the draws (set to lucky #13 for now, could set to be rand(1,21) later)
        if (plotsdisp == TRUE) {
            plot(density(rawcampyconc$V13))
        }

return(rawcampyconc)

}

# Check that it works
rawcampyconc = draw_campy(nMC = nMC, plotsdisp = T) # Units of CFU/L

```

### Draw for Giardia
```{r draw_giardia}

# See "fitenvdata_forQMRAinputs" file for code used to find fit parameters
# We'll use meanlog = 0.6408606, sdlog = 0.7579550; units of oocysts/100 L --> per Lucas (1998)
# 14% prevalence (point value)

# Function inputs:
#  nMC: the number of monte carlo draws to carry out
#  plotsdisp: whether to display a summary plot of one of the refill draws
#  Distribution parameters (prevalence and concentration) are initialized within the function

# Function outputs:
#  rawgiardiaconc: a 21 x nMC dataframe where each column is nMC draws for giardia concentration for a given water refill
#  Note: rawgiardiaconc has units of oocysts/L


draw_giardia = function(nMC, plotsdisp) {
    # Step 1: create data frame with cocnentrations of Giardia
    list = list() #create an empty list
    
    # Populate data frame
    # See "fitenvdata_forQMRAinputs" code for code and data used to find fit parameters
    # We'll use meanlog = 0.6408606, sdlog = 0.7579550; units of oocysts/100 L --> per Lucas (1998)
    # 14% prevalence (point value)
        for (i in 1:21) {
            vec = numeric(nMC) #preallocate a numeric vector
            vec = rlnorm(nMC, meanlog = 0.6408606, sdlog = 0.7579550) # Units in oocysts/100 L
            list[[i]]  = vec
        }
    # data wrangling
    rawgiardiaconc = do.call("rbind",list)
    rawgiardiaconc = as.data.frame(rawgiardiaconc)
    rawgiardiaconc = t(sapply(rawgiardiaconc, as.numeric))
    rawgiardiaconc = as.data.frame(rawgiardiaconc)

    # Step 2: randomly replace 14.2857142857143% of the samples with 0 (see summary spreadsheet with data from Lucas et al)
    # https://stackoverflow.com/questions/70401107/r-randomly-changing-values-in-a-dataframe
    # https://stackoverflow.com/questions/72313629/r-randomly-replace-values-with-na
    # In cases where values are replaced with zero, instead replace them with a value from a PDF to reflect the LDL of Campy sampling
    # For giardia, the LDL is 1 oocyst/100 L, so 0.01 CFU in 1 L.  
    # Make function to replace some % of values with a non-detect
    FUNgiardia = function(x) {
        censvaluegiardia = runif(1, min = 0, max = 1) # Define non-detect value; units in oocysts/100 L
        probgiardia = 0.142857142857143 # Define giardia prevalence
        sample(c(x, censvaluegiardia), 1, prob=c(probgiardia,(1 - probgiardia))) # Randomly replace 14% of values with a non-detct
        }
    rawgiardiaconc <- as.data.frame(apply(rawgiardiaconc, 1:2, FUNgiardia ))  # Units in oocysts/100 L
    rawgiardiaconc = rawgiardiaconc/100  # Get in units of oocysts/1 L


    #Visualise one of the refills (set to lucky #13 for now, could set to be rand(1,21) later)
    if (plotsdisp == TRUE) {
    plot(density(rawgiardiaconc$V13))
    }
    
    # Output value
    return(rawgiardiaconc)
}

# Check that it works
rawgiardiaconc = draw_giardia(nMC = nMC, plotsdisp = T) # Units of oocysts/1 L

```

## Populate dataframes with an LRV
```{r make LRV dataframe}

## Function to make a matrix out of a given LRV
# Simply takes an input LRV and makes an nxn dataframe populated with it
# Used to make an 21 x nMC dataframe of LRVs for calculations

# Inputs
#   LRV: point value to be replicated into dataframe
#   nrows: how many rows in the df, should be nMC
#   ncols: how many columns in the df, should be 21

# Outputs
#   LRVs: an ncols x nrows dataframe populated with LRV in every cell

FUNmakeLRVmx = function(LRV, nrows, ncols){
    
    LRVs = rep(LRV, times = nrows)
    LRVs = data.frame(LRVs)
    LRVs = cbind(LRVs, rep(LRVs[1], (ncols-1)))
    colnames(LRVs) = 1:ncol(LRVs)
    return(LRVs)
    
}



#Check using the first entry of the LRVs_forsummary input data table
LRVs_Ecoli = FUNmakeLRVmx(LRV = 4.19, nrows = nMC, ncols = 21)
LRVs_yeast = FUNmakeLRVmx(LRV = 3.73, nrows = nMC, ncols = 21)

```

## Draw for drinking water consumption in each "DW event" (Refill)
```{r draw_DW_consumption}

# Based on curve fitting of survey data, we can assume that reported DW consumed in a day follows a truncated normal distribution
# mean = 0.816667 L, SD = 0.3496667 L, lower limit = 0.25 L **This is per water refill, NOT per day** (21 refills in a 7-day trip)
# see "fitenvdata_forQMRA" R code for how those parameters were generated


## Define function to make MC draws for water consumed per refill
# Inputs
#   nMC: the number of monte carlo draws to carry out
#   plotsdisp: whether to display a summary plot of one of the refill draws
#   Distribution parameters (volume of water consumed per refill) are initialized within the function
# Outputs
#   DWvol: a 21 x nMC dataframe populated for draws of the volume of water consumed per refill 
#          Units in L per refill (21 refills in a 7-day trip)


drawDW = function(nMC, plotsdisp){

    list = list() #create an empty list
    
    # Make nMC draws for volume of water consumed per refill
    for (i in 1:21) {
        vec = numeric(nMC) #preallocate a numeric vector
        mean = 2.446786*(1/3)
        sd = 1.049*(1/3)
        vec = rtruncnorm(n = nMC, a = 0.25, b = Inf, mean = mean, sd = sd) # Trunate at 0.25 L, or half of the mean
        list[[i]]  = vec
    }
    
    # Wrangle data
    DWvol = do.call("rbind",list)
    DWvol = as.data.frame(DWvol)
    DWvol = t(sapply(DWvol, as.numeric))
    DWvol = as.data.frame(DWvol)
    
    #Visualise one of the draws (set to lucky #13 for now, could set to be rand(1,21) later)
    if (plotsdisp == TRUE) {
    plot(density(DWvol$V13))
    }
    
    # DWvol units in L per refill (21 refills per 7-day trip)
    return(DWvol)

}

# Check that it works
DWvol = drawDW(nMC = nMC, plotsdisp = T)

```

## Calculate pathogen exposure per DW event and over the 7-day backpacking trip
```{r calc_exposure}

### Step 1: Calculate exposure in each of the 21 DW refills
## Reminder: conc of campy and giardia should be #/L before feeding to this function
# I.e., raworgconc should be in units of organisms per liter

# Define function to calculate the exposure to a given pathogen during each of the 21 refills
# Inputs
#   LRVs: a 21 x nMC dataframe populated with the point-value LRV for the water treatment device (see chunk "Populate dataframes with LRV")
#   raworgconc: a 21 x nMC dataframe populated with the MC draws for pathogen concentration in water (units of #/L)
#               see the "Draw for campylobacter" and "draw for giardia" chunks
#   DWvol: a 21 x nMC dataframe populated with the nMC draws for water volume consumed per refill (units of L per refill)
# Outputs
#   exposure: a 21 x nMC dataframe with each cell containing the number of pathogens consumed per refill


calc_exposure = function(LRVs, raworgconc, DWvol, plotsdisp) {
    
    # Step 1: Calculate what the pathogen concentration will be in the drinking water
    survival = 10^(-1*LRVs) # Units as a % of the number in the raw water [unitless]
    DW_orgconc = raworgconc * survival # Units of #organisms/1 L
    
    # Step 2: Exposure per draw of water
    # exposure = volume of water consumed in the draw [L] * pathogen concentration in that water [#/L]
    exposure = DWvol * DW_orgconc # Units of #organisms drunk in the refill event
    
    if (plotsdisp == TRUE) {
    plot(density(exposure$V13))
    }
    
    # exposure is the number of pathogens consumed per refill (units of #/refill)
    return(exposure)
    
}

# Check it works
exposure_campy = calc_exposure(LRVs = LRVs_Ecoli, raworgconc = rawcampyconc, DWvol = DWvol, plotsdisp = T)  # Units of CFU campylobacter drunk in the refill event
exposure_giardia = calc_exposure(LRVs = LRVs_yeast, raworgconc = rawgiardiaconc, DWvol = DWvol, plotsdisp = T)  # Units of Giardia oocysts drunk in the refill event


## Step 2: Sum across all 21 DW refills --> this will be the total pathogens consumed in a 7-day backpacking trip
# Note: This is the first of three model endpoints

# Define a function to calculate the total number of pathogens consumed in a 7-day backpacking trip
# Inputs
#   exposure: the output from the function calc_exposure, 21 x nMC matrix with each cell as the number of pathogens consumed per refills
# Outputs
#   exposure_trip: the total number of pathogens consumed in a 7-day backpacking trip (units of # of pathogens)

calc_tripexposure = function(exposure, plotsdisp) {
    
    # Sum all the 21 exposures across the rows
    exposure_trip = exposure %>%
        mutate(sum = rowSums(.[1:21]))
    exposure_trip = exposure_trip$sum
    
    #Display
    if (plotsdisp == TRUE) {
        plot(density(exposure_trip))  
    }
    
    # Output is exposure_trip, total number of pathogens consumed per trip
    return(exposure_trip)
}

# Check it works
exposure_campy_trip = calc_tripexposure(exposure = exposure_campy, plotsdisp = T)  # Units of total CFU campylobacter drunk on a 7-day backpacking trip
exposure_giardia_trip = calc_tripexposure(exposure = exposure_giardia, plotsdisp = T)  # Units of Giardia oocysts drunk on a 7-day backpacking trip

```


## Calculate P(inf) per refill
```{r calc_Pinf_refill}

## Campylobacter ## 

# From Medema (1996) we have a MLE Beta-Poisson model with alpha = 0.145 and N50 = 890
# This model is not used by Murphy (2016) but is used by Bivins (2019) -- although he also uses the Teunis model

# NOTE: maybe put in the Teunis model and weight them 50/50? For later

# Define function to calculate the probability of infection with Campylobacter per refill
# Inputs
#   exposure_campy: a 21 x nMC dataframe with each cell containing the number of campylobacter consumed per refill
#                   see chunk "calc_exposure" for details
# Outputs
#   Pinf_campy: a 21 x nMC with each cell containing the Pinf with campylobacter per refill

Pinf_c = function(exposure_campy, plotsdisp) {
    
    # Define Pinf parameters
    alpha = 0.145
    N50 = 890
    beta = 7.59
    
    # Calculate Pinf_campy
    Pinf_campy = 1 - (1+(exposure_campy*((2^(1/alpha) - 1)/N50)))^(-1*alpha)
    
    # Plot lucky #13
        if (plotsdisp == TRUE) {
            plot(density(Pinf_campy$V13))
        }
    # Return output
    return(Pinf_campy)
}

# Check it works
Pinf_campy = Pinf_c(exposure_campy = exposure_campy, plotsdisp = T)

## Giardia ##

# Rose et al (1991) is used by Murphy (2016) and recommended by WHO (2016)
# Exponential calculation with r = 0.0199

# Define function to calculate the probability of infection with Giardia per refill
# Inputs
#   exposure_giardia: a 21 x nMC dataframe with each cell containing the number of giardia consumed per refill
#                   see chunk "calc_exposure" for details
# Outputs
#   Pinf_giardia: a 21 x nMC with each cell containing the Pinf with giardia per refill  

Pinf_g = function(exposure_giardia, plotsdisp) {
    
    # Define Pinf parameters
    r = 0.0199
    
    # Calculate Pinf
    Pinf_giardia = 1-exp(-1*r*exposure_giardia)
    
    # Plot lucky #13
        if (plotsdisp == TRUE) {
            plot(density(Pinf_giardia$V13))
        }
    # Return output
    return(Pinf_giardia)
}

# Check it works
Pinf_giardia = Pinf_g(exposure_giardia = exposure_giardia, plotsdisp = T)
```


## Calculate total P(inf) for the 7-day trip
```{r calc_Pinf_trip}

## Calculate the overall probability of infection for the 7-day backpacking trip 
# Note: This is the second of three model endpoints
# Formula -->  Pinf_trip = 1 - [(1-Pinf, refill 1)*(1-Pinf, refill 2)...*(1-Pinf, refill 21)]

# Define function to do calculation
# Inputs
#   Pinf: a 21 x nMC with each cell containing the Pinf with the pathogen per refill
# Outputs
#   Pinf_trip: a 1 x nMC dataframe with the overall probability of infection for the 7-day backpacking trip (unitless)

Pinf_trip = function(Pinf, plotsdisp) {
    
    # Do calculations
    Pinf_oneminus = 1-Pinf
    Pinf_trip = Pinf_oneminus %>%
        mutate(prod = Reduce(`*`, .))
    Pinf_trip = Pinf_trip$prod
    Pinf_trip = 1-Pinf_trip
    
    # Plot
    if (plotsdisp == TRUE) {
        plot(density(Pinf_trip))  
    }
    
    # Return output
    return(Pinf_trip)
}

# Check it works
Pinf_campy_trip = Pinf_trip(Pinf = Pinf_campy, plotsdisp = T)  # Probability of infection with Campylobacter for a 7-day backpacking trip
Pinf_giardia_trip = Pinf_trip(Pinf = Pinf_giardia, plotsdisp = T)  # Probability of infection with Campylobacter for a 7-day backpacking trip

```


```{r calc_Pill_given_Pinf}

# Define function to populate a dataframe with the probability of illness given infection, Pillinf
# Pillinf is a decimal (i.e., % chance), from 0.1 to 0.6 for Campy and 0.2 to 0.7 for Giardia

# Pill = Pinf*Pillinf
# Use Pillinf from Murphy (2016): a uniform distribution (originally from USEPA, 2010)
# Campy has min = 0.1, max = 0.6
# Giardia has min = 0.2, max = 0.7

# Inputs
#   nMC: the number of monte carlo draws to carry out
#   min: the mimimum of the uniform distribution of Pillinf
#   max: the maximum of the uniform distribution of Pillinf
# Outputs
#   Pillinf: the probability of having a symptomatic illness given Pinf
#   This will be used in the DALY calculation



Pill_given_Pinf = function(nMC, min, max, plotsdisp) {
    Pillinf = runif(nMC, min = min, max = max) # Probability of illness given infection
    # Display
    if (plotsdisp == TRUE) {
        plot(density(Pillinf))  
    }
    return(Pillinf)
}

## Try the function out
# Campy
Pill_given_Pinf_campy = Pill_given_Pinf(nMC = nMC, min = 0.1, max = 0.6 , plotsdisp = T)
Pill_trip_campy = Pinf_campy_trip * Pill_given_Pinf_campy
# Giardia
Pill_given_Pinf_giardia = Pill_given_Pinf(nMC = nMC, min = 0.2, max = 0.7 , plotsdisp = T)
Pill_trip_giardia = Pinf_giardia_trip * Pill_given_Pinf_giardia

```


## Calculate DALYs per trip
```{r calc_DALYs}

# Define function to calculate the total DALYs per 7-day backpacking trip

# DALYs per illness = Pill * S * DW * number of people or life years (per Bivins 2019)
# Where:
# Pill was calculated in the last chunk


# Inputs
#   Pill_trip: the overall probability of having a symptomatic illness from the 7-day backpacking trip
#   S: the susceptible fraction; for both campy and giardia, S = 100%
#   DW: DALY weighting, the expected DALY weight per illness/case
#   n_campingtrips: how many camping trips to calculate for. For our purposes here, it will always be 1 but if we were calculating DALYs on a                      per summer basis it could be the number of people hiking the JDF per summer
# Outputs
#   DALYs: Total DALYs per 7-day backpacking trip

calcDALYs = function(Pill_trip, S, DW, n_campingtrips, plotsdisp) {
    
    # Calculations
    DALYs = Pill_trip * S * DW * n_campingtrips
    
    # Display
    if (plotsdisp == TRUE) {
        plot(density(DALYs))  
    }
    # Output
    return(DALYs)
}


## Try the function out
# Initialize values
# DW_campy = 4.6 per 1000 cases --> From WHO (2016), used in Bivins (2019)
DW_campy = 4.6/1000 # Units of DALY per illness case
# DW_giardia = 1.7 per 1000 cases --> From Health Canada (2012)
DW_giardia = 1.7/1000   # Units of DALY per illness case
# 100% susceptibility
S = 1
# If n_campingtrips = 1, then the DALYs are in units of DALY per person per camping trip
n_campingtrips = 1

# Use functions
DALY_campy = calcDALYs(Pill_trip = Pill_trip_campy, S = S, DW = DW_campy, n_campingtrips = n_campingtrips, plotsdisp = T)  # Units of YLL per year of backpackers hiking
DALY_giardia = calcDALYs(Pill_trip = Pill_trip_giardia, S = S, DW = DW_giardia, n_campingtrips = n_campingtrips, plotsdisp = T)  # Units of YLL per year of backpackers hiking

```


## Calculate endpoints given MC drawn inputs
```{r calc_endpoints}


# Define function to calculate the QMRA endpoints (dose, Pinf, DALYs)

## Inputs:
# LRV and microbe (campy or giardia)
# MC draws: WQ conc = raw water pathogen concentration
#           DW vol = water vol drunk per refill
#           Pillgiven inf = probability of illnes given infection with either campy or giardia
#           all 21 x nMC dataframes with MC draws
# Other point values: S = susceptability fraction (100% for campy and giardia)
#                     n_campingtrips = number of camping trips (1 for our study)
#                     DALY_weight = DALY weighting per illness
#                     nMC = number of monte carlo draws    

## Outputs:
# endpoints dataframe, which is 5 x nMC, containing:
# endpoint_exposure = endpoint #1, total pathogen ingestion over the backpacking trip 
# endpoint_Pinf = endpoint #2, probability of infection from the 7-day backpacking trip  
# endpoint_DALY = endpoint #3, DALYs from the 7-day trip
# process_rawWQtrip = for sensitivity analysis, total pathogens in raw water over the 7-day backpacking trip
# process_DWvoltrip = for sensitivity analysis, total water volume drunk over the 7-day trip


calc_endpoints = function(S, n_campingtrips, DALY_weight, nMC,  # Point values
                          DW_conc, DWvol, Pillinf,      # 21 x nMC dataframes populated via MC draws
                          LRV, microbe) {                       # Point values for microbe
    
    # Populate LRV matrix
    LRVmx = FUNmakeLRVmx(LRV = LRV, nrows = nMC, ncols = 21)
    
    
    # Calculate dose (endpoint #1)
    #   a: Calculate dose per refill
    exposure = calc_exposure(LRVs = LRVmx, raworgconc = DW_conc, DWvol = DWvol, plotsdisp = F) # Units of organisms/L
    #   b: Calculate total dose over the 7-day trip
    tripexposure = calc_tripexposure(exposure = exposure, plotsdisp = F)  # Units of total organisms drunk per trip
    
    
    # Calculate Pinf (endpoint #2)
    #   a: Use dose-response calculation for each refill
    if(microbe == "Ecoli"){  
        # Campylobacter dose-response
        Pinf = Pinf_c(exposure = exposure, plotsdisp = F)
        
    } else {
        # Giardia dose-response
        Pinf = Pinf_g(exposure = exposure, plotsdisp = F)
    }
    #   b: Calculate the overall Pinf for the trip
    Pinf_trip = Pinf_trip(Pinf = Pinf, plotsdisp = F)
    
    
    # Calculate DALYs per trip (endpoint #3)
    #    a: Calculate the Pill, using Pillinf
    Pill_trip = Pinf_trip * Pillinf
    #    b: Calculate DALYs (units of YLL)
    DALY_trip = calcDALYs(Pill_trip = Pill_trip, 
                          S = S, 
                          DW = DALY_weight, 
                          n_campingtrips = n_campingtrips, 
                          plotsdisp = F)
    
    
    ## Calculation for later correlations analysis
    # Total microbes in raw water over the trip
    DW_conc = DW_conc %>%
        mutate(sum = rowSums(.[1:21]))
    DW_raw_trip = DW_conc$sum
    # Total DW drunk over the trip
    DWvol = DWvol %>%
        mutate(sum = rowSums(.[1:21]))
    DWvol_trip = DWvol$sum
    
    
    # Wrangle data
    endpoints = tibble(tripexposure, Pinf_trip, DALY_trip, # endpoints
                       DW_raw_trip, DWvol_trip) %>%        # For correlations
        rename(
            endpoint_exposure = tripexposure, 
            endpoint_Pinf = Pinf_trip, 
            endpoint_DALY = DALY_trip,
            process_rawWQtrip = DW_raw_trip,
            process_DWvoltrip = DWvol_trip
        )

    
    # Return output
    return(endpoints)
    
}

# Try the function
try_endpoints_campy = calc_endpoints(S = S, n_campingtrips = n_campingtrips, DALY_weight = DALY_campy, nMC = nMC,
                                 DW_conc = rawcampyconc, DWvol = DWvol, Pillinf = Pill_given_Pinf_campy,
                                 LRV = 4, microbe = "Ecoli")

```



# Part II:  Put all the functions together to do the QMRA
## Do one QMRA for a manuf-field LRV pair
```{r do one QMRA for one lab vs field pair}

#### Define function to compare lab vs field QMRA for a given lab-field pair of data for a given device
# This function will be used in the next chunk in a for loop

# Inputs:
#   nMC: the number of monte carlo draws to carry out
#   LRV_manuf: point-value LRV claimed by manufacturers
#   LRV_field: point-value LRV obtained in 2021 field study
#   microbe: either "campy" or "giardia"

# Outputs
# the oneQMRA dataframe, which is 13 x (2 x nMC), containing:
# info_surveynum = which survey the data pair comes from (should be one campy and one giardia per survey)
# info_pairnum = which lab-field data pair the data belong to
# info_treatmenttype = "chemical", "filter" or "UV"
# info_treatmentname = which treatment device was used
# info_organism = "campy" or "giardia'
# info_setting = "manuf" or "field"
# input_LRV = the point-value LRV 
# process_DWvoltrip = explained in above chunk
# process_rawWQtrip = explained in above chunk
# process_Pillinf = probability of illness given infection
# endpoint_exposure = explained in above chunk
# endpoint_Pinf = explained in above chunk
# endpoint_DALY = explained in above chunks


doQMRA_labvfield = function(nMC, LRV_manuf, LRV_field, microbe) {
    
    
    ## Do MC draws: WQ_conc, DW_vol, Pillinf
    # DW_conc, Pillinf, depend on the choice of microbe
    # Draw for DWvol
    DWvol = drawDW(nMC = nMC, plotsdisp = F)
    
    # Draw for WQ_conc and Pillinf
    if(microbe == "Ecoli"){  
        # Campylobacter 
        WQ_conc = draw_campy(nMC = nMC, plotsdisp = F)
        Pillinf = Pill_given_Pinf(nMC = nMC, min = 0.1, max = 0.6, plotsdisp = F) # Murphy (2016), originally from USEPA (2010)
        DALYweight = 4.6/1000 # Units of DALY per illness case --> From WHO (2016), used in Bivins (2019)
        
    } else {
        # Giardia dose-response
        WQ_conc = draw_giardia(nMC = nMC, plotsdisp = F)
        Pillinf = Pill_given_Pinf(nMC = nMC, min = 0.2, max = 0.7, plotsdisp = F) # Murphy (2016), originally from USEPA (2010)
        DALYweight = 1.7/1000   # Units of DALY per illness case --> From Health Canada (2012)
    }
    
    
    ## Calculate endpoints, using LRV_manuf and LRV_field
    # Using LRV_field
    endpoints_field = calc_endpoints(nMC = nMC, 
                                     S = 1, 
                                     n_campingtrips = 1, 
                                     DALY_weight = DALYweight, 
                                     DWvol = DWvol,
                                     DW_conc = WQ_conc, 
                                     Pillinf = Pillinf,
                                     LRV = LRV_field, 
                                     microbe = microbe)
    # USing LRV_manuf
    endpoints_manuf = calc_endpoints(nMC = nMC, 
                                     S = 1, 
                                     n_campingtrips = 1, 
                                     DALY_weight = DALYweight, 
                                     DWvol = DWvol,
                                     DW_conc = WQ_conc, 
                                     Pillinf = Pillinf,
                                     LRV = LRV_manuf, 
                                     microbe = microbe)
    

    
    ## Wrangle data
    
    # add setting names ("field" or "manuf") to both endpoints tables
    # Also Pillinf so that we can do correlations analysis later
    # And the input LRV (field or manuf)
    endpoints_field = endpoints_field %>%
        mutate(info_setting = "field", .before = endpoint_exposure) %>%
        mutate(process_Pillinf = Pillinf) %>%
        mutate(input_LRV = LRV_field, .after = info_setting)
    endpoints_manuf = endpoints_manuf %>%
        mutate(info_setting = "manuf", .before = endpoint_exposure) %>%
        mutate(process_Pillinf = Pillinf) %>%
        mutate(input_LRV = LRV_manuf, .after = info_setting)
    
    # Use rbind to make one big dataframe
    endpoints = rbind(endpoints_field, endpoints_manuf)
    
    # Output
    oneQMRA = endpoints
    return(oneQMRA)
    
}

# Try one QMRA
tryoneQMRA = doQMRA_labvfield(nMC = nMC,
                              LRV_manuf = 4, LRV_field = 2,
                              microbe = "Ecoli")

```


## Do a for loop for QMRA for all manuf-field LRV pairs
```{r cycle through all the manuf-field LRV pairs - this is the overall QMRA}


# Initialize
nMC = 10000
allQMRA = tibble()

# Do for loop
for(i in 1:nrow(rawLRVdata)) {
    
    # Check
    print(i)
    
    # Initialize row i
    row <- rawLRVdata[i,]
    
    # Call function to do QMRA
    oneQMRA = doQMRA_labvfield(nMC = nMC,
                               LRV_manuf = row$LRV_manuf, 
                               LRV_field = row$LRV_field,
                               microbe = row$organism
                              )
    
    # Wrangle data
    oneQMRA = oneQMRA %>%
        mutate(info_surveynum = row$row_num) %>%  # Indicates which survey the data belong to, so that yeast/ecoli could be paired
        mutate(info_pairnum = i) %>%
        mutate(info_treatmenttype = row$treatment_type) %>%
        mutate(info_treatmentname = row$treatment_name) %>%
        mutate(info_organism = row$organism)
        
    
    # Output
    allQMRA = rbind(allQMRA, oneQMRA)
}

# Reorganize column order
allQMRA = allQMRA %>%
    dplyr::select(info_surveynum,
                  info_pairnum,
                  info_treatmenttype,
                  info_treatmentname,
                  info_organism,
                  info_setting,
                  
                  input_LRV,
                  
                  process_DWvoltrip,
                  process_rawWQtrip,
                  process_Pillinf,
                  
                  endpoint_exposure,
                  endpoint_Pinf,
                  endpoint_DALY
                  )


# pivot longer (needed for making figures below, and correlations analysis)
allQMRA_long = allQMRA %>%
    pivot_longer(
            cols = starts_with("endpoint"),
            names_to = "endpoint_name",
            values_to = "endpoint_value",
            names_prefix = "endpoint_"
    ) 


```


# Figures for publication
## Data wrangling
```{r wrangle data for figures}

### Wrangle data more, to figure out the difference in lab vs field endpoints
allQMRA_graph = allQMRA_long %>%
    pivot_wider(                    # Pivot wider so that manuf - field can be calculated
        names_from = info_setting,
        values_from = c(endpoint_value, input_LRV)
    ) %>%
    dplyr::select(                  # Select the relevant columns
                  info_surveynum,
                  info_pairnum,
                  info_treatmenttype,
                  info_treatmentname,
                  info_organism,

                  input_LRV_field,
                  input_LRV_manuf,
                  
                  endpoint_name,
                  endpoint_value_field,
                  endpoint_value_manuf,
                  ) 
    
# Subtract endpoints to find the difference
# Take endpoint_field - endpoint_manuf
# and LRV_field - LRV_manuf
# So that if LRV_manuf > LRV_field, then the difference in health risk would be positive
# and difference in LRV would be negative
allQMRA_graph = allQMRA_graph %>%
    mutate(endpoint_value_subtract = endpoint_value_field - endpoint_value_manuf) %>%
    mutate(input_LRV_subtract = input_LRV_field - input_LRV_manuf, .after = input_LRV_manuf)


### Calculate overall means for graphing
# Get means
allQMRA_graphmeans = allQMRA_graph %>%
    group_by(info_organism, info_treatmenttype, endpoint_name) %>%      # Tell R to group means by these variables
    summarise(
        n = n(), 
        endpoint_value_subtract_mean = mean(endpoint_value_subtract)    # Get mean values
    ) %>%
    mutate(endpoint_value_subtract_mean_yval = 1)         # Initialize the column for yvalues corresponding to that mean


# Get corresponding y-values for those means
# Do a for loop
for(i in 1:nrow(allQMRA_graphmeans)) {
    # Check
    print(i)

    # Initialize row i
    row <- allQMRA_graphmeans[i,]
    
    # Get corresponding y-value
    yval = ecdf(
        filter(allQMRA_graph,
               info_organism == row$info_organism, 
               info_treatmenttype == row$info_treatmenttype, 
               endpoint_name == row$endpoint_name)$endpoint_value_subtract
    )(row$endpoint_value_subtract_mean)

    # Put into allQMRA_graphmeans dataframe under yvalues
    allQMRA_graphmeans[i, "endpoint_value_subtract_mean_yval"] = yval
}


### Graph setup 
# Establish colour palette, from Rcolourbrewer palette "RdYlBu"
brew_11 = c("#A50026",
            "#D73027",
            "#F46D43",
            "#FDAE61",
            "#FEE090",
            "#FFFFBF",
            "#E0F3F8",
            "#ABD9E9",
            "#74ADD1",
            "#4575B4",
            "#313695")
brew_3 = c("#A50026", "#FC8D59", "#4575B4")
fill_3 = c("#DB99A8","#FED1BD","#B5C8E1")

# Make facet label names
treatment_type_labs = c("a) Chemical disinfection", "b) Filtration", "c) UV disinfection")
names(treatment_type_labs) = c("chemical", "filter", "UV")


```


## Campylobacter figure
```{r campy figure, fig.width= 8, fig.height=11}


## Draw graph for exposure
plot_subtractendp_exposure_c = ggplot() +
                            
                            # Plot ecdf lines for each lab-field data pair
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "Ecoli"  & endpoint_name == "exposure"), 
                                    aes(endpoint_value_subtract, 
                                        colour = info_treatmenttype, 
                                        group = info_pairnum), 
                                    geom = "step", linewidth = 0.15, alpha = 0.55) +
    
                            # Plot ecdf line for all data together
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "Ecoli"  & endpoint_name == "exposure"), 
                                    aes(endpoint_value_subtract, colour = info_treatmenttype),
                                    geom = "step", linewidth = 0.85, alpha = 1)+

                            # Create 3 panels, one for each treatment type (filter/chemical/UV)
                            facet_wrap( ~ info_treatmenttype, ncol = 1,
                                    labeller = labeller(info_treatmenttype = treatment_type_labs)) +
    
                            # Define scales 
                            scale_x_continuous(trans='pseudo_log',
                                       limits = c(-10, 10000),
                                       breaks = c(-10, -1, 0, 1, 10, 100, 1000, 10000),
                                       minor_breaks = c(-5, -0.5, 0.5, 5, 50, 500, 5000),
                                       labels = c("-10", "-1", "0",
                                                  "+1", "+10", "+100", "+1000", "+10000"))+
                            scale_y_continuous(breaks = c(0.1, 0.5, 0.9), limits = c(0, NA)) +
    
                            # Define axis labels
                            xlab(paste("Difference in dose", "", "", sep = "")) +
                            ylab("") +
    
                            # Draw dashed lines at the 10% and 90% percentiles
                            geom_hline(yintercept = 0.1, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
                            geom_hline(yintercept = 0.9, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
    
                            # Draw diamond shapes for mean values
                            geom_point(data = filter(allQMRA_graphmeans, info_organism == "Ecoli"  & endpoint_name == "exposure"),
                                       aes(x = endpoint_value_subtract_mean, 
                                           y = endpoint_value_subtract_mean_yval, 
                                           colour = info_treatmenttype, 
                                           fill = info_treatmenttype),
                                       shape = 23, size = 2.5, stroke = 1.5
                                       ) +
    
                            # Define aesthetic values such as colour
                            theme_bw() +
                            scale_color_manual(values = brew_3) +
                            scale_fill_manual(values = fill_3) +
                            theme(legend.position = "none",
                                  text = element_text(size = 12), 
                                  axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1),
                                  axis.title.x = element_text(size=12),
                                  panel.grid.minor = element_blank(), 
                                  strip.background = element_rect(fill = "white", color = NA),
                                  strip.text.x = element_text(hjust = 0, vjust = 1, size = 12))
plot(plot_subtractendp_exposure_c)



## Draw graph for Pinf
plot_subtractendp_Pinf_c = ggplot() +
                            
                            # Plot ecdf lines for each lab-field data pair
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "Ecoli"  & endpoint_name == "Pinf"), 
                                    aes(endpoint_value_subtract, 
                                        colour = info_treatmenttype, 
                                        group = info_pairnum), 
                                    geom = "step", linewidth = 0.15, alpha = 0.55) +
    
                            # Plot ecdf line for all data together
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "Ecoli"  & endpoint_name == "Pinf"), 
                                    aes(endpoint_value_subtract, colour = info_treatmenttype),
                                    geom = "step", linewidth = 0.85, alpha = 1)+

                            # Create 3 panels, one for each treatment type (filter/chemical/UV)
                            facet_wrap( ~ info_treatmenttype, ncol = 1,
                                    labeller = labeller(info_treatmenttype = treatment_type_labs)) +
    
                            # Define scales 
                            scale_x_continuous(trans='pseudo_log',
                                               breaks = seq(from = -0.5, to = 1, by = 0.5),
                                               limits = c(-0.5, 1)) +
                            scale_y_continuous(breaks = c(0.1, 0.5, 0.9), limits = c(0, NA)) +
    
                            # Define axis labels
                            xlab(paste("Difference in", "probability of infection", sep = "\n")) +
                            ylab("") +
    
                            # Draw dashed lines at the 10% and 90% percentiles
                            geom_hline(yintercept = 0.1, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
                            geom_hline(yintercept = 0.9, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
    
                            # Draw diamond shapes for mean values
                            geom_point(data = filter(allQMRA_graphmeans, info_organism == "Ecoli"  & endpoint_name == "Pinf"),
                                       aes(x = endpoint_value_subtract_mean, 
                                           y = endpoint_value_subtract_mean_yval, 
                                           colour = info_treatmenttype, 
                                           fill = info_treatmenttype),
                                       shape = 23, size = 2.5, stroke = 1.5
                                       ) +
    
                            # Define aesthetic values such as colour
                            theme_bw() +
                            scale_color_manual(values = brew_3) +
                            scale_fill_manual(values = fill_3) +
                            theme(legend.position = "none",
                                  text = element_text(size = 12), 
                                  axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1),
                                  axis.title.x = element_text(size=12),
                                  panel.grid.minor = element_blank(), 
                                  strip.background = element_rect(fill = "white", color = NA),
                                  strip.text.x = element_text(colour = "white", hjust = 0, vjust = 1, size = 12)
                                  # NOTE: strip.text.x being set to white keeps the labels but turns the font white 
                                  # so that the plot sizing is unchanged but each facet row isn't labelled 3 times 
                                  # when we get to the patchwork step (below). Delete if you want the text back
                                  )
plot(plot_subtractendp_Pinf_c)




## Draw graph for DALYs
plot_subtractendp_DALY_c = ggplot() +
                            
                            # Plot ecdf lines for each lab-field data pair
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "Ecoli"  & endpoint_name == "DALY"), 
                                    aes(endpoint_value_subtract, 
                                        colour = info_treatmenttype, 
                                        group = info_pairnum), 
                                    geom = "step", linewidth = 0.15, alpha = 0.55) +
    
                            # Plot ecdf line for all data together
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "Ecoli"  & endpoint_name == "DALY"), 
                                    aes(endpoint_value_subtract, colour = info_treatmenttype),
                                    geom = "step", linewidth = 0.85, alpha = 1)+

                            # Create 3 panels, one for each treatment type (filter/chemical/UV)
                            facet_wrap( ~ info_treatmenttype, ncol = 1,
                                    labeller = labeller(info_treatmenttype = treatment_type_labs)) +
    
                            # Define scales 
                            scale_x_continuous(trans='pseudo_log',
                                       limits = c(-0.001, 0.002),
                                       breaks = c(-0.001, 0, 0.001, 0.002),
                                       minor_breaks = c(-0.0005, 0.0005, 0.0015),
                                       labels = c("-0.001", "0", "0.001", "0.002")
                                       ) +
                            scale_y_continuous(breaks = c(0.1, 0.5, 0.9), limits = c(0, NA)) +
    
                            # Define axis labels
                            xlab(paste("Difference in DALYs", "", "", sep = "")) +
                            ylab("") +
    
                            # Draw dashed lines at the 10% and 90% percentiles
                            geom_hline(yintercept = 0.1, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
                            geom_hline(yintercept = 0.9, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
    
                            # Draw diamond shapes for mean values
                            geom_point(data = filter(allQMRA_graphmeans, info_organism == "Ecoli"  & endpoint_name == "DALY"),
                                       aes(x = endpoint_value_subtract_mean, 
                                           y = endpoint_value_subtract_mean_yval, 
                                           colour = info_treatmenttype, 
                                           fill = info_treatmenttype),
                                       shape = 23, size = 2.5, stroke = 1.5
                                       ) +
    
                            # Define aesthetic values such as colour
                            theme_bw() +
                            scale_color_manual(values = brew_3) +
                            scale_fill_manual(values = fill_3) +
                            theme(legend.position = "none",
                                  text = element_text(size = 12), 
                                  axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1),
                                  axis.title.x = element_text(size=12),
                                  panel.grid.minor = element_blank(), 
                                  strip.background = element_rect(fill = "white", color = NA),
                                strip.text.x = element_text(colour = "white", hjust = 0, vjust = 1, size = 12)
                                  # NOTE: strip.text.x being set to white keeps the labels but turns the font white 
                                  # so that the plot sizing is unchanged but each facet row isn't labelled 3 times 
                                  # when we get to the patchwork step (below). Delete if you want the text back)
                                  )
plot(plot_subtractendp_DALY_c)



# Put all 3 figures together with Patchwork
plot_subtractendp_all_c = plot_subtractendp_exposure_c + plot_subtractendp_Pinf_c + plot_subtractendp_DALY_c +
    plot_annotation(
        title = paste("Subtract endpoints between field-obtained", 
                      "and manufacturer-claimed LRV scenarios ",
                       sep = " "), 
        subtitle = expression(paste(italic("C. jejuni")))) & 
    theme(plot.title = element_text(size = 14, hjust = 0),    # Left-aligned
          plot.subtitle = element_text(size = 12, hjust = 0)) # Left-aligned
plot(plot_subtractendp_all_c)


# Save figure for publication
ggsave("output_QMRA/subtractendpoints_campy.png", 
        plot = plot_subtractendp_all_c,
        dpi = 300,
        width = 8.5,
        height = 11,
        units = "in")

```



## Giardia figure
```{r giardia figure, fig.width= 8, fig.height=11}


## Draw graph for exposure
plot_subtractendp_exposure_g = ggplot() +
                            
                            # Plot ecdf lines for each lab-field data pair
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "yeast"  & endpoint_name == "exposure"), 
                                    aes(endpoint_value_subtract, 
                                        colour = info_treatmenttype, 
                                        group = info_pairnum), 
                                    geom = "step", linewidth = 0.15, alpha = 0.55) +
    
                            # Plot ecdf line for all data together
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "yeast"  & endpoint_name == "exposure"), 
                                    aes(endpoint_value_subtract, colour = info_treatmenttype),
                                    geom = "step", linewidth = 0.85, alpha = 1)+

                            # Create 3 panels, one for each treatment type (filter/chemical/UV)
                            facet_wrap( ~ info_treatmenttype, ncol = 1,
                                    labeller = labeller(info_treatmenttype = treatment_type_labs)) +
    
                            # Define scales 
                            scale_x_continuous(trans='pseudo_log',
                                       limits = c(-0.005, 0.02)
                                       ) +
                            scale_y_continuous(breaks = c(0.1, 0.5, 0.9), limits = c(0, NA)) +
    
                            # Define axis labels
                            xlab(paste("Difference in dose", "", "", sep = "")) +
                            ylab("") +
    
                            # Draw dashed lines at the 10% and 90% percentiles
                            geom_hline(yintercept = 0.1, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
                            geom_hline(yintercept = 0.9, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
    
                            # Draw diamond shapes for mean values
                            geom_point(data = filter(allQMRA_graphmeans, info_organism == "yeast"  & endpoint_name == "exposure"),
                                       aes(x = endpoint_value_subtract_mean, 
                                           y = endpoint_value_subtract_mean_yval, 
                                           colour = info_treatmenttype, 
                                           fill = info_treatmenttype),
                                       shape = 23, size = 2.5, stroke = 1.5
                                       ) +
    
                            # Define aesthetic values such as colour
                            theme_bw() +
                            scale_color_manual(values = brew_3) +
                            scale_fill_manual(values = fill_3) +
                            theme(legend.position = "none",
                                  text = element_text(size = 12), 
                                  axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1),
                                  axis.title.x = element_text(size=12),
                                  panel.grid.minor = element_blank(), 
                                  strip.background = element_rect(fill = "white", color = NA),
                                  strip.text.x = element_text(hjust = 0, vjust = 1, size = 12))
plot(plot_subtractendp_exposure_g)


## Draw graph for Pinf
plot_subtractendp_Pinf_g = ggplot() +
                            
                            # Plot ecdf lines for each lab-field data pair
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "yeast"  & endpoint_name == "Pinf"), 
                                    aes(endpoint_value_subtract, 
                                        colour = info_treatmenttype, 
                                        group = info_pairnum), 
                                    geom = "step", linewidth = 0.15, alpha = 0.55) +
    
                            # Plot ecdf line for all data together
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "yeast"  & endpoint_name == "Pinf"), 
                                    aes(endpoint_value_subtract, colour = info_treatmenttype),
                                    geom = "step", linewidth = 0.85, alpha = 1)+

                            # Create 3 panels, one for each treatment type (filter/chemical/UV)
                            facet_wrap( ~ info_treatmenttype, ncol = 1,
                                    labeller = labeller(info_treatmenttype = treatment_type_labs)) +
    
                            # Define scales 
                            scale_x_continuous(trans='pseudo_log',
                                       limits = c(-0.00025, 0.00075),
                                       breaks = c(-0.00025, 0, 0.00025, 0.0005, 0.00075),
                                       labels = c(expression(-2.5%.%10^{-4}),
                                           "0",
                                           expression(2.5%.%10^{-4}),
                                           expression(5.0%.%10^{-4}),
                                           expression(7.5%.%10^{-4}))
                                       ) +
                            scale_y_continuous(breaks = c(0.1, 0.5, 0.9), limits = c(0, NA)) +
    
                            # Define axis labels
                            xlab(paste("Difference in", "probability of infection", sep = "\n")) +
                            ylab("") +
    
                            # Draw dashed lines at the 10% and 90% percentiles
                            geom_hline(yintercept = 0.1, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
                            geom_hline(yintercept = 0.9, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
    
                            # Draw diamond shapes for mean values
                            geom_point(data = filter(allQMRA_graphmeans, info_organism == "yeast"  & endpoint_name == "Pinf"),
                                       aes(x = endpoint_value_subtract_mean, 
                                           y = endpoint_value_subtract_mean_yval, 
                                           colour = info_treatmenttype, 
                                           fill = info_treatmenttype),
                                       shape = 23, size = 2.5, stroke = 1.5
                                       ) +
    
                            # Define aesthetic values such as colour
                            theme_bw() +
                            scale_color_manual(values = brew_3) +
                            scale_fill_manual(values = fill_3) +
                            theme(legend.position = "none",
                                  text = element_text(size = 12), 
                                  axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1),
                                  axis.title.x = element_text(size=12),
                                  panel.grid.minor = element_blank(), 
                                  strip.background = element_rect(fill = "white", color = NA),
                                  strip.text.x = element_text(colour = "white", hjust = 0, vjust = 1, size = 12)
                                  # NOTE: strip.text.x being set to white keeps the labels but turns the font white 
                                  # so that the plot sizing is unchanged but each facet row isn't labelled 3 times 
                                  # when we get to the patchwork step (below). Delete if you want the text back
                                  )
plot(plot_subtractendp_Pinf_g)



## Draw graph for DALYs
plot_subtractendp_DALY_g = ggplot() +
                            
                            # Plot ecdf lines for each lab-field data pair
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "yeast"  & endpoint_name == "DALY"), 
                                    aes(endpoint_value_subtract, 
                                        colour = info_treatmenttype, 
                                        group = info_pairnum), 
                                    geom = "step", linewidth = 0.15, alpha = 0.55) +
    
                            # Plot ecdf line for all data together
                            stat_ecdf(data = filter(allQMRA_graph, info_organism == "yeast"  & endpoint_name == "DALY"), 
                                    aes(endpoint_value_subtract, colour = info_treatmenttype),
                                    geom = "step", linewidth = 0.85, alpha = 1)+

                            # Create 3 panels, one for each treatment type (filter/chemical/UV)
                            facet_wrap( ~ info_treatmenttype, ncol = 1,
                                    labeller = labeller(info_treatmenttype = treatment_type_labs)) +
    
                            # Define scales 
                            scale_x_continuous(trans='pseudo_log',
                                       limits = c((-0.5*10^-7),
                                                  (1*10^-7)),
                                       breaks = c((-5*10^-8),
                                                  # (-1*10^-6),
                                                  0,
                                                  (5*10^-8),
                                                  (1*10^-7)),
                                       labels = c(
                                           expression(-5%.%10^{-8}),
                                           "0",
                                           expression(5%.%10^{-8}),
                                           expression(1%.%10^{-7}))
                                       ) +
                            scale_y_continuous(breaks = c(0.1, 0.5, 0.9), limits = c(0, NA)) +
    
                            # Define axis labels
                            xlab(paste("Difference in DALYs", "", "", sep = "")) +
                            ylab("") +
    
                            # Draw dashed lines at the 10% and 90% percentiles
                            geom_hline(yintercept = 0.1, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
                            geom_hline(yintercept = 0.9, linetype = "dashed", colour = "black", size = 0.5, alpha = 0.75) +
    
                            # Draw diamond shapes for mean values
                            geom_point(data = filter(allQMRA_graphmeans, info_organism == "yeast"  & endpoint_name == "DALY"),
                                       aes(x = endpoint_value_subtract_mean, 
                                           y = endpoint_value_subtract_mean_yval, 
                                           colour = info_treatmenttype, 
                                           fill = info_treatmenttype),
                                       shape = 23, size = 2.5, stroke = 1.5
                                       ) +
    
                            # Define aesthetic values such as colour
                            theme_bw() +
                            scale_color_manual(values = brew_3) +
                            scale_fill_manual(values = fill_3) +
                            theme(legend.position = "none",
                                  text = element_text(size = 12), 
                                  axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1),
                                  axis.title.x = element_text(size=12),
                                  panel.grid.minor = element_blank(), 
                                  strip.background = element_rect(fill = "white", color = NA),
                                strip.text.x = element_text(colour = "white", hjust = 0, vjust = 1, size = 12)
                                  # NOTE: strip.text.x being set to white keeps the labels but turns the font white 
                                  # so that the plot sizing is unchanged but each facet row isn't labelled 3 times 
                                  # when we get to the patchwork step (below). Delete if you want the text back)
                                  )
plot(plot_subtractendp_DALY_g)



# Put all 3 figures together with Patchwork
plot_subtractendp_all_g = plot_subtractendp_exposure_g + plot_subtractendp_Pinf_g + plot_subtractendp_DALY_g +
    plot_annotation(
        title = paste("Subtract endpoints between field-obtained", 
                      "and manufacturer-claimed LRV scenarios ",
                       sep = " "), 
        subtitle = expression(paste(italic("G. lamblia")))) & 
    theme(plot.title = element_text(size = 14, hjust = 0),    # Left-aligned
          plot.subtitle = element_text(size = 12, hjust = 0)) # Left-aligned
plot(plot_subtractendp_all_g)



# Save figure for publication
ggsave("output_QMRA/subtractendpoints_giardia.png", 
        plot = plot_subtractendp_all_g,
        dpi = 300,
        width = 8.5,
        height = 11,
        units = "in")


```


# QMRA summary tables for publication SI
## By treatment category: UV/filter/chemical
```{r summary tables}

### Data wrangling
## NOTE: This is a bit repeated from the chunk "wrangle data for figures" but I didn't want to use the same df so I'm redoing it here
# Wrangle data wider, to figure out the difference in lab vs field endpoints
allQMRA_forsummary = allQMRA_long %>%
    pivot_wider(                    # Pivot wider so that manuf - field can be calculated
        names_from = info_setting,
        values_from = c(endpoint_value, input_LRV)
    ) %>%
    rename(                         # Rename columns to match our naming scheme
        endpoint_field = endpoint_value_field,
        endpoint_manuf = endpoint_value_manuf,
        LRV_field = input_LRV_field,
        LRV_manuf = input_LRV_manuf
        ) %>%
    dplyr::select(                  # Select the relevant columns
                  info_surveynum,
                  info_pairnum,
                  info_treatmenttype,
                  info_treatmentname,
                  info_organism,

                  LRV_field,
                  LRV_manuf,
                  
                  endpoint_name,
                  endpoint_field,
                  endpoint_manuf,
                  ) 
    
# Subtract endpoints to find the difference
# Take endpoint_field - endpoint_manuf
# and LRV_field - LRV_manuf
# So that if LRV_manuf > LRV_field, then the difference in health risk would be positive
# and difference in LRV would be negative
allQMRA_forsummary = allQMRA_forsummary %>%
    mutate(endpoint_subtract = endpoint_field - endpoint_manuf) %>%
    mutate(LRV_subtract = LRV_field - LRV_manuf, .after = LRV_manuf)


# Pivot_longer again, so that we can group_by setting
allQMRA_forsummary = allQMRA_forsummary %>%
  pivot_longer(cols = -c(info_surveynum, info_pairnum, info_treatmenttype, info_treatmentname, info_organism, endpoint_name),
               names_to = c(".value","location"),
               names_pattern = "(LRV|endpoint)_(manuf|field|subtract)",
               values_to = c("value", "type")) %>%
    
    rename(                         # Rename columns to match our naming scheme
        endpoint_value = endpoint,
        LRV_value = LRV,
        info_setting = location
    )




### Calculate summary stats for summary table
summarytable_output = allQMRA_forsummary %>%
    # Group and calc stats
    group_by(info_organism, info_setting, info_treatmenttype, endpoint_name) %>%      # Tell R to group means by these variables
    summarise(
        nsurveys = n()/nMC, 
        endpoint_mean = mean(endpoint_value),                   # Get mean values
        endpoint_10 = quantile(endpoint_value, probs = 0.1),    # 10th percentile
        endpoint_50 = quantile(endpoint_value, probs = 0.5),    # 50th percentile (median)
        endpoint_90 = quantile(endpoint_value, probs = 0.9),     # 90th percentile 
        LRV_mean = mean(LRV_value)
    ) %>%

    # Pivot this table wider, so that each column contains an endpoint summary stat for exp/Pinf/DALY
    pivot_wider(
        names_from = endpoint_name,
        values_from = c(endpoint_mean, endpoint_10, endpoint_50, endpoint_90)
    ) %>%
    
    # Make a new column with proper pathogen names
    mutate(
        gt_organism = case_when(
                    info_organism == "Ecoli" ~ " C. jejuni",
                    info_organism == "yeast" ~ "G. lamblia"
        ), .after = info_organism
    ) %>%
    
    # Make another new column with proper setting names
    mutate(
        gt_setting = case_when(
                    info_setting == "field" ~ "Fieldwork 2021",
                    info_setting == "manuf" ~ "Manufacturer claim",
                    info_setting == "subtract" ~ "Difference between field and manufacturer"
        ), .after = info_setting
    ) %>%
    
    # Make another new column with proper treatment type names
    mutate(
        gt_treatmenttype = case_when(
            info_treatmenttype == "UV" ~ "UV",
            info_treatmenttype == "chemical" ~ "Chemical",
            info_treatmenttype == "filter" ~ "Filter"
        ), .after = info_treatmenttype
    )



### Make summary table using gt 
summarytable_output %>%
    # Wrangle data
    ungroup() %>%
    dplyr::select(-c(info_organism, info_setting, info_treatmenttype)) %>%
    
    # Tell it to do a gt table
    # Also specify to divide the table according to organism and setting
    gt(groupname_col = "gt_organism",
       rowname_col = "gt_setting"
    ) %>%
    
    # Scientific formatting
    fmt_scientific(
        columns = starts_with("endpoint"),
        decimals = 2
    ) %>%
    
    # Number formatting
    fmt_number(
        columns = LRV_mean,
        decimals = 2
    ) %>%

    
    # Make table spanners
    tab_spanner(
        label = "Dose",
        columns = ends_with("exposure")
    ) %>%
    tab_spanner(
        label = "Probability of infection",
        columns = ends_with("Pinf")
    ) %>%
    tab_spanner(
        label = "DALYs",
        columns = ends_with("DALY")
    ) %>%
    
    # Rename columns
    cols_label(
        gt_treatmenttype = "Treatment type",
        nsurveys = "Number of surveys",
        LRV_mean = "Mean LRV",
        
        endpoint_mean_exposure = "Mean",
        endpoint_10_exposure = "10th Percentile", 
        endpoint_50_exposure = "50th Percentile (Median)", 
        endpoint_90_exposure = "90th Percentile", 
        
        endpoint_mean_Pinf = "Mean",
        endpoint_10_Pinf = "10th Percentile", 
        endpoint_50_Pinf = "50th Percentile (Median)", 
        endpoint_90_Pinf = "90th Percentile", 
        
        endpoint_mean_DALY = "Mean",
        endpoint_10_DALY = "10th Percentile", 
        endpoint_50_DALY = "50th Percentile (Median)", 
        endpoint_90_DALY = "90th Percentile"

    ) %>%

    # Do aesthetics 
    cols_align(align = "left") %>%
    tab_style(
        style = cell_text(style = "italic"),
        locations = cells_row_groups(groups = c(1,2))
        ) %>%
    
    # Save
    gtsave("output_QMRA/summarytable.docx")



```




## By treatment device name (so 104 x 3 x 2 rows)
```{r summary tables by device name}

### Data wrangling
## NOTE: This is a bit repeated from the chunk "wrangle data for figures" but I didn't want to use the same df so I'm redoing it here
# Wrangle data wider, to figure out the difference in lab vs field endpoints
allQMRA_forsummary_treatmentdev  = allQMRA_long %>%
    pivot_wider(                    # Pivot wider so that manuf - field can be calculated
        names_from = info_setting,
        values_from = c(endpoint_value, input_LRV)
    ) %>%
    rename(                         # Rename columns to match our naming scheme
        endpoint_field = endpoint_value_field,
        endpoint_manuf = endpoint_value_manuf,
        LRV_field = input_LRV_field,
        LRV_manuf = input_LRV_manuf
        ) %>%
    dplyr::select(                  # Select the relevant columns
                  info_surveynum,
                  info_pairnum,
                  info_treatmenttype,
                  info_treatmentname,
                  info_organism,

                  LRV_field,
                  LRV_manuf,
                  
                  endpoint_name,
                  endpoint_field,
                  endpoint_manuf,
                  ) 
    
# Subtract endpoints to find the difference
# Take endpoint_field - endpoint_manuf
# and LRV_field - LRV_manuf
# So that if LRV_manuf > LRV_field, then the difference in health risk would be positive
# and difference in LRV would be negative
allQMRA_forsummary_treatmentdev  = allQMRA_forsummary_treatmentdev  %>%
    mutate(endpoint_subtract = endpoint_field - endpoint_manuf) %>%
    mutate(LRV_subtract = LRV_field - LRV_manuf, .after = LRV_manuf)


# Pivot_longer again, so that we can group_by setting
allQMRA_forsummary_treatmentdev  = allQMRA_forsummary_treatmentdev  %>%
  pivot_longer(cols = -c(info_surveynum, info_pairnum, info_treatmenttype, info_treatmentname, info_organism, endpoint_name),
               names_to = c(".value","location"),
               names_pattern = "(LRV|endpoint)_(manuf|field|subtract)",
               values_to = c("value", "type")) %>%
    
    rename(                         # Rename columns to match our naming scheme
        endpoint_value = endpoint,
        LRV_value = LRV,
        info_setting = location
    )




### Calculate summary stats for summary table
summarytable_output_treatmentdev = allQMRA_forsummary_treatmentdev %>%
    # Group and calc stats
    group_by(info_organism,               # Tell R to group means by these variables
             info_setting, 
             info_treatmenttype, 
             info_treatmentname, 
             endpoint_name) %>%
    summarise(
        n_datapoints = n()/nMC,                                 # Get the number of surveys with that respective device
        endpoint_mean = mean(endpoint_value),                   # Get mean values
        endpoint_10 = quantile(endpoint_value, probs = 0.1),    # 10th percentile
        endpoint_50 = quantile(endpoint_value, probs = 0.5),    # 50th percentile (median)
        endpoint_90 = quantile(endpoint_value, probs = 0.9),    # 90th percentile 
        LRV_mean = mean(LRV_value)                              # Get the mean LRV
    ) %>%
    pivot_wider(
        names_from = endpoint_name,
        values_from = c(endpoint_mean, endpoint_10, endpoint_50, endpoint_90)
    ) %>%
    
    # Make a new column with proper pathogen names
    mutate(
        gt_organism = case_when(
                    info_organism == "Ecoli" ~ " C. jejuni",
                    info_organism == "yeast" ~ "G. lamblia"
        ), .after = info_organism
    ) %>%
    
    # Make another new column with proper setting names
    mutate(
        gt_setting = case_when(
                    info_setting == "field" ~ "Fieldwork 2021",
                    info_setting == "manuf" ~ "Manufacturer claim",
                    info_setting == "subtract" ~ "Difference between field and manufacturer"
        ), .after = info_setting
    ) %>%
    
    # Make another new column with proper treatment type names
    mutate(
        gt_treatmenttype = case_when(
            info_treatmenttype == "UV" ~ "UV",
            info_treatmenttype == "chemical" ~ "Chemical",
            info_treatmenttype == "filter" ~ "Filter"
        ), .after = info_treatmenttype
    ) %>%
    
    # Make another new column with proper names for the treatment devices
    mutate(
        gt_treatmentname = case_when(
            info_treatmentname == "aquatabs" ~ "Aquatabs",
            info_treatmentname == "aquatabs_20L" ~ "Aquatabs, 20L",
            info_treatmentname == "grayl" ~ "Grayl",
            info_treatmentname == "katadyn_basecamppro10L" ~ "Katadyn Base Camp Pro, 10 L",
            info_treatmentname == "katadyn_befree" ~ "Katadyn BeFree", 
            info_treatmentname == "katadyn_hikerpro" ~ "Katadyn Hiker Pro",
            info_treatmentname == "katadyn_vario" ~ "Katadyn Vario",
            info_treatmentname == "lifestraw_flex" ~ "Lifestraw Flex",
            info_treatmentname == "miniwell_L630" ~ "Miniwell L630",
            info_treatmentname == "MSR_autoflow" ~ "MSR Autoflow",
            info_treatmentname == "MSR_guardian" ~ "MSR Guardian",
            info_treatmentname == "MSR_hyperflow" ~ "MSR Hyperflow",
            info_treatmentname == "MSR_miniworks" ~ "MSR Miniworks",
            info_treatmentname == "MSR_trailshot" ~ "MSR Trailshot",
            info_treatmentname == "platypus_gravityworks" ~ "Platypus GravityWorks",
            info_treatmentname == "printine_filter" ~ "Pristine Filter",
            info_treatmentname == "pristine_drops" ~ "Pristine Drops",
            info_treatmentname == "sawyer_microsqueeze" ~ "Sawyer Micro Squeeze",
            info_treatmentname == "sawyer_mini" ~ "Sawyer Mini",
            info_treatmentname == "sawyer_squeeze" ~ "Sawyer Squeeze",
            info_treatmentname == "steripen" ~ "SteriPen",
            info_treatmentname == "survivor_prox" ~ "Survivor Pro X",
            info_treatmentname == "versa_flow" ~ "Versa Flow"
        ), .after = info_treatmentname
    )



### Make summary table using gt 
summarytable_output_treatmentdev %>%
    # Wrangle data
    ungroup() %>%
    dplyr::select(-c(info_organism, info_setting, info_treatmenttype, info_treatmentname)) %>%
    
    # Tell it to do a gt table
    # Also specify to divide the table according to organism and setting
    gt(groupname_col = "gt_organism",
       rowname_col = "gt_setting"
    ) %>%
    
    # Scientific formatting
    fmt_scientific(
        columns = starts_with("endpoint"),
        decimals = 2
    ) %>%
    
    # Format LRV column
    fmt_number(
        columns = LRV_mean,
        decimals = 2
    ) %>%
    
    # Make table spanners
    tab_spanner(
        label = "Dose",
        columns = ends_with("exposure")
    ) %>%
    tab_spanner(
        label = "Probability of infection",
        columns = ends_with("Pinf")
    ) %>%
    tab_spanner(
        label = "DALYs",
        columns = ends_with("DALY")
    ) %>%
    
    # Rename columns
    cols_label(
        gt_treatmenttype = "Treatment type",
        gt_treatmentname = "Device name",
        n_datapoints = "Number of surveys",
        LRV_mean = "Mean LRV",
        
        endpoint_mean_exposure = "Mean",
        endpoint_10_exposure = "10th Percentile", 
        endpoint_50_exposure = "50th Percentile (Median)", 
        endpoint_90_exposure = "90th Percentile", 
        
        endpoint_mean_Pinf = "Mean",
        endpoint_10_Pinf = "10th Percentile", 
        endpoint_50_Pinf = "50th Percentile (Median)", 
        endpoint_90_Pinf = "90th Percentile", 
        
        endpoint_mean_DALY = "Mean",
        endpoint_10_DALY = "10th Percentile", 
        endpoint_50_DALY = "50th Percentile (Median)", 
        endpoint_90_DALY = "90th Percentile"

    ) %>%

    # Do aesthetics 
    cols_align(align = "left") %>%
    tab_style(
        style = cell_text(style = "italic"),
        locations = cells_row_groups(groups = c(1,2))
        ) %>%
    
    # Save
    gtsave("output_QMRA/summarytable_bytreatmentdevice.docx")


```


# Sensitivity analysis
## Rough correlations analysis
```{r correlations analysis, fig.width= 11, fig.height=8}

### Data wrangling
# Wrangle data longer, so that the process column values are all one column
allQMRA_forcorr = allQMRA_long %>%
    rename(process_LRV = input_LRV) %>%  # Rename LRV column so it'll get pivoted 
    pivot_longer(
        cols = starts_with("process"),
        names_to = "process_name",
        values_to = "process_value",
        names_prefix = "process_"
    ) %>%
    
    # Filter out the endpoints that don't use Pillinf
    filter(
        !(process_name == "Pillinf" & endpoint_name == "exposure"),
        !(process_name == "Pillinf" & endpoint_name == "Pinf")
    )



### Correlations
# Calculate
corr_summ = allQMRA_forcorr %>%
    # Wrangle
    group_by(info_organism, process_name, endpoint_name) %>%
    
    # Make corr and R2 calculations
    summarize(
        corr = cor(process_value, endpoint_value, method = "sp"), 
        R2 = corr^2
    ) 


# Wrangle for gt table
corr_summ_gt = corr_summ %>%
    # Make a new column with proper pathogen names
    mutate(
        gt_organism = case_when(
                    info_organism == "Ecoli" ~ " C. jejuni",
                    info_organism == "yeast" ~ "G. lamblia"
        ), .after = info_organism
    ) %>%
    
    # Make new column with proper endpoint names
    mutate(
        gt_endpoint_name = case_when(
            endpoint_name == "exposure" ~ "Exposure",
            endpoint_name == "Pinf" ~ "Probability of infection",
            endpoint_name == "DALY" ~ "DALYs"
        ), .after = endpoint_name
    ) %>%
    
    # Make new column with input variable names and units
    mutate(
        gt_process_name = case_when(
           process_name == "DWvoltrip" ~ "Total drinking water consumed (L)",
           process_name == "LRV" ~ "LRV (unitless)",
           process_name == "Pillinf" ~ "Probability of illness given infection (unitless)",
           process_name == "rawWQtrip" ~ "Total raw water pathogen concentration (CFU or oocysts/L)"
        ), .after = process_name
    )
    
    

# Make summary table
corr_summ_gt %>%
    # Wrangle
    ungroup() %>%
    dplyr::select(-c(R2, info_organism, endpoint_name, process_name)) %>%
    group_by(gt_organism) %>%
    
    # Make table
    gt() %>%
    
    # Move endpoint_name column to the front
    cols_move_to_start(
        columns = gt_endpoint_name
    ) %>%
    
    # Format corr column
    fmt_number(
        columns = c(corr),
        decimals = 4
    ) %>%
    
    # Rename columns
    cols_label(
        gt_endpoint_name = "QMRA endpoint",
        gt_process_name = "Input variable (units)",
        corr = "Spearman correlation, rho"
    ) %>%

    # Do aesthetics 
    cols_align(align = "left") %>%
    tab_style(
        style = cell_text(style = "italic"),
        locations = cells_row_groups()
        ) 
    
    # Save
    # gtsave("output_QMRA/summarytable_corr.docx")


### Graphing
# Initialize colour aesthetics
brew_3 = c("#A50026", "#FC8D59", "#4575B4")
fill_3 = c("#DB99A8","#FED1BD","#B5C8E1")

# Make labels
allQMRA_forcorr$endpoint_name = factor(allQMRA_forcorr$endpoint_name,
                                       levels = c("exposure", "Pinf", "DALY"), 
                                       labels = c("Exposure (#/L)",
                                                  "Probability of illness (unitless)",
                                                  "DALYs"))
allQMRA_forcorr$process_name = factor(allQMRA_forcorr$process_name, 
                                      levels = c("rawWQtrip", "LRV", "DWvoltrip", "Pillinf"),
                                      labels = c(paste("Total raw water pathogen", "concentration (#/L)", sep = "\n"),
                                                 "LRV (unitless)",
                                                 paste("Total drinking water", "consumed (L)", sep = "\n"),
                                                 paste("Probability of illness", "given infection (unitless)", sep = "\n")))

# Campylobacter
corr_plot_campy = ggplot(data = filter(allQMRA_forcorr, info_organism == "Ecoli"),
                         aes(x = process_value, y = endpoint_value, colour = endpoint_name)) +
    geom_point(size = 1, alpha = 0.5) +
    geom_line(stat = "smooth", 
              method = "lm", 
              alpha = 1, 
              size = 1) +
    facet_grid(endpoint_name ~ process_name, 
               scales = "free",
               switch = "y") +
    theme_bw() +
    scale_color_manual(values = brew_3) +
    theme(axis.title = element_blank(),
          # panel.spacing.x = unit(1,"lines"), 
          legend.position = "none",
          text = element_text(size = 12), 
          axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1),
          panel.grid.minor = element_blank(), 
          strip.background = element_rect(fill = "white", color = NA),
          strip.text.x = element_text(size = 12),
          strip.text.y = element_text(size = 12)
          ) +
    scale_y_continuous(position = "right")
    
plot(corr_plot_campy)

# Save figure for publication
ggsave("output_QMRA/correlationplot_campy.png", 
        plot = corr_plot_campy,
        dpi = 300,
        width = 11,
        height = 8.5,
        units = "in")


# Giardia
corr_plot_giardia = ggplot(data = filter(allQMRA_forcorr, info_organism == "yeast"),
                         aes(x = process_value, y = endpoint_value, colour = endpoint_name)) +
    geom_point(size = 1, alpha = 0.5) +
    geom_line(stat = "smooth", 
              method = "lm", 
              alpha = 1, 
              size = 1) +
    facet_grid(endpoint_name ~ process_name, 
               scales = "free",
               switch = "y") +
    theme_bw() +
    scale_color_manual(values = brew_3) +
    theme(axis.title = element_blank(),
          # panel.spacing.x = unit(1,"lines"), 
          legend.position = "none",
          text = element_text(size = 12), 
          axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1),
          panel.grid.minor = element_blank(), 
          strip.background = element_rect(fill = "white", color = NA),
          strip.text.x = element_text(size = 12),
          strip.text.y = element_text(size = 12)
          ) +
    scale_y_continuous(position = "right")
    
plot(corr_plot_giardia)

# Save figure for publication
ggsave("output_QMRA/correlationplot_giardia.png", 
        plot = corr_plot_giardia,
        dpi = 300,
        width = 11,
        height = 8.5,
        units = "in")

```