---
title: "sensitivity_tornado"
author: "Camille Zimmer"
date: "2024-03-11"
output: html_document
---


#  *** NOTE *** This markdown is archived, the content has been moved to the markdown "labvsfield_QMRA.Rmd", chunks 21 through 30



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


#Clear environment
# rm(list = ls())

#Load libraries
library(tidyverse)       # For tidy datasets and graphing 
# library(fitdistrplus)    # For fitting distributions
# library(readxl)          # For reading excel files
# library(writexl)         # For writing excel files
library(mc2d)            # For monte carlo draws
# library(truncnorm)       # To draw from a truncated normal distribution
library(patchwork)       # For graphing, to stitch multiple graphs together
library(RColorBrewer)    # For making nicely coloured graphs
# library(gt)              # For making summary tables

# Define number of Monte Carlo observations we want per draw (currently 100 for the first chunks, will be redefined further down)
nMC = 100
```



# Make function to do a deterministic QMRA based on point-value inputs
```{r deterministic QMRA}

### Make function to calculate QMRA endpoints based on point-value inputs that were stochastic in our overall QMRA model
# Inputs:
#   rawpathconc = the pathogen concentration in the raw water, in organisms/L
#   DWvol = the volume of water consumed in each refill (21 refills per 7-day backpacking trip), in L
#   LRV = the treatment device LRV with respect to each pathogen, unitless
#   Pillinf = the probability of illness given infection with a pathogen, unitless
#   microbe: either "campy" or "giardia"

# Outputs:
#   det_QMRA: A 7 x 1 tibble containing all the calculated deterministic endpoints (trip exposure, Pinf on the trip, DALYs per trip)
#             as well as the inputs (rawpathconc, DWvol, LRV, Pillinf)

# Process variables (were point-value in our overall QMRA model):
#   Dose-response relationship: For campylobacter, Pinf follows an approximate Beta-Poisson model with alpha = 0.144 and N50 = 890, per Medema (1996). For giardia, Pinf follows an exponential model with r = 0.0199, per Rose (1991)
#   DALY weight (DALY_weight): DALYS per illness, for campylobacter is 4.6E-3, and for giardia is 1.7E-3, per USEPA (2010)
#   Susceptible fraction (S): Susceptible fraction of the population, 100% for both campylobacter and giradia

FUN_detQMRA = function(rawpathconc, DWvol, LRV, Pillinf, microbe){
    
    ### Endpoint 1: overall trip exposure
    # Calculate the exposure per refill
    survival_frac = 10^(-1*LRV)     # Units are a % of the number of pathogens in the raw water (unitless)
    DW_conc_refill = rawpathconc * survival_frac * DWvol     # The number of pathogens in each refill (units of # pathogens)
    
    # Calculate the exposure over the 7-day trip (21 refills) --> First endpoint
    exposure_trip = DW_conc_refill * 7    # Units of # pathogens/7-day trip
    
    
    ### Endpoint #2: Probability of infection
    #   a: Use dose-response calculation for each refill
    if(microbe == "campy"){  
        # Campylobacter dose-response
        Pinf_refill = Pinf_c(exposure = exposure_trip, plotsdisp = F)
    } else {
        # Giardia dose-response
        Pinf_refill = Pinf_g(exposure = exposure_trip, plotsdisp = F)
    }
    #   b: Calculate the overall Pinf for the trip --> second endpoint
    Pinf_trip = 1 - (1 - Pinf_refill)^21
    
    
    ### Endpoint #3: DALYs per 7-day trip
    #    a: Calculate the Pill, using Pillinf
    Pill_trip = Pinf_trip * Pillinf
    
    #    b: Determine DALY weighting, depending on if campy or giardia
    if(microbe == "campy"){ 
        DALY_weight = 4.6E-3
    } else {
        DALY_weight = 1.7E-3
    }
    
    #    c: Calculate DALYs (units of YLL)
    DALY_trip = calcDALYs(Pill_trip = Pill_trip, 
                          S = 1,       # 100% susceptibility 
                          DW = DALY_weight, 
                          n_campingtrips = 1,   # One camping trip
                          plotsdisp = F)
    
    
    ### Wrangle outputs
    det_QMRA = tibble(microbe, rawpathconc, DWvol, LRV, Pillinf,          # Inputs
                    exposure_trip, Pinf_trip, DALY_trip) %>%              # Endpoints
        rename(
            info_organism = microbe,
            input_rawpathconc = rawpathconc,
            input_DWvol = DWvol,
            input_LRV = LRV,
            input_Pillinf = Pillinf,
            
            endpoint_exposure = exposure_trip, 
            endpoint_Pinf = Pinf_trip, 
            endpoint_DALY = DALY_trip
        )
    
    # Output
    return(det_QMRA)
    
    
}



try_detQMRA = FUN_detQMRA(rawpathconc = 10, 
                      DWvol = 0.5,
                      LRV = 2,
                      Pillinf = 0.2,
                      microbe = "giardia")

```



# Make function to take the 10,000 MC-drawn inputs and figure out the percentile information
```{r pull percentile information from MC-drawn inputs}

### Make function to take our QMRA model inputs and figure out what the percentile information is

# Inputs:
#   allQMRA = a 13 x 4,180,000 dataframe with the QMRA results (see the chunk "cycle through all manuf-field LRV pairs")
#   percentile = a decimal value for the percentile that is to be calculated (i.e., 0.9 for the 90th/10th percentiles)

# Outputs:
#   input_percentiles: a 3 x 8 dataframe containing the input_name (the name of the input value), the input_value (the value itself), and percentile (what percentile we're looking at, and also the 50th percentile or median) 

FUN_inputpercentiles = function(QMRAdf, percentile){
    
    oneminuspercentile = 1 - percentile
    
    ### Get percentiles
    # Get df for campy and giardia
    QMRAdf_campy = filter(QMRAdf, QMRAdf$info_organism == "Ecoli")
    QMRAdf_giardia = filter(QMRAdf, QMRAdf$info_organism == "yeast")
    
    ## Raw water conc percentiles (total throughout the trip) 
    # Campy
    upper_rawpathconc_campy = quantile(QMRAdf_campy$process_rawWQtrip, probs = percentile)
    mid_rawpathconc_campy = quantile(QMRAdf_campy$process_rawWQtrip, probs = 0.5)
    lower_rawpathconc_campy = quantile(QMRAdf_campy$process_rawWQtrip, probs = oneminuspercentile)
    # Giardia
    upper_rawpathconc_giardia = quantile(QMRAdf_giardia$process_rawWQtrip, probs = percentile)
    mid_rawpathconc_giardia = quantile(QMRAdf_giardia$process_rawWQtrip, probs = 0.5)
    lower_rawpathconc_giardia = quantile(QMRAdf_giardia$process_rawWQtrip, probs = oneminuspercentile)
    
    
    ## Total drinking water volume over the trip
    upper_DWvol = quantile(QMRAdf$process_DWvoltrip, probs = percentile)
    mid_DWvol = quantile(QMRAdf$process_DWvoltrip, probs = 0.5)
    lower_DWvol = quantile(QMRAdf$process_DWvoltrip, probs = oneminuspercentile)
    
    ## LRV
    # Campy
    upper_LRV_campy = quantile(QMRAdf_campy$input_LRV, probs = percentile)
    mid_LRV_campy = quantile(QMRAdf_campy$input_LRV, probs = 0.5)
    lower_LRV_campy = quantile(QMRAdf_campy$input_LRV, probs = oneminuspercentile)
    # Giardia
    upper_LRV_giardia = quantile(QMRAdf_giardia$input_LRV, probs = percentile)
    mid_LRV_giardia = quantile(QMRAdf_giardia$input_LRV, probs = 0.5)
    lower_LRV_giardia = quantile(QMRAdf_giardia$input_LRV, probs = oneminuspercentile)
    
    
    ## Probability of illness given infection 
    # Campy
    upper_Pillinf_campy = quantile(QMRAdf_campy$process_Pillinf, percentile)
    mid_Pillinf_campy = quantile(QMRAdf_campy$process_Pillinf, 0.5)
    lower_Pillinf_campy = quantile(QMRAdf_campy$process_Pillinf, oneminuspercentile)
    # Giardia
    upper_Pillinf_giardia = quantile(QMRAdf_giardia$process_Pillinf, percentile)
    mid_Pillinf_giardia = quantile(QMRAdf_giardia$process_Pillinf, 0.5)
    lower_Pillinf_giardia = quantile(QMRAdf_giardia$process_Pillinf, oneminuspercentile)
    
    
    ### Wrangle outputs
    # Make nice tibble
    info_organism = c(rep("campy", 12), rep("giardia", 12))
    input_name = rep(c(rep("rawpathconc", 3),
                       rep("DWvol", 3),
                       rep("LRV", 3),
                       rep("Pillinf", 3)), 2)
    input_value = c(upper_rawpathconc_campy, mid_rawpathconc_campy, lower_rawpathconc_campy,   # Campy values
                    upper_DWvol, mid_DWvol, lower_DWvol, 
                    upper_LRV_campy, mid_LRV_campy, lower_LRV_campy, 
                    upper_Pillinf_campy, mid_Pillinf_campy, lower_Pillinf_campy,
                    
                    upper_rawpathconc_giardia, mid_rawpathconc_giardia, lower_rawpathconc_giardia,   # Giardia values
                    upper_DWvol, mid_DWvol, lower_DWvol, 
                    upper_LRV_giardia, mid_LRV_giardia, lower_LRV_giardia, 
                    upper_Pillinf_giardia, mid_Pillinf_giardia, lower_Pillinf_giardia
                    )
    percentile_values = c(rep(c(percentile, 0.5, oneminuspercentile), 8))
    nicepercentiles = tibble(info_organism, input_name, input_value, percentile_values)
    print(nicepercentiles)
    
    ## Make actual tibble that will go into a for loop later
    # Campy
    rawpathconc_campy = c(mid_rawpathconc_campy, upper_rawpathconc_campy, lower_rawpathconc_campy, rep(mid_rawpathconc_campy, 8))
    DWvol = c(rep(mid_DWvol, 3), upper_DWvol, lower_DWvol, rep(mid_DWvol, 6))
    LRV_campy = c(rep(mid_LRV_campy, 5), upper_LRV_campy, lower_LRV_campy, rep(mid_LRV_campy, 4))
    Pillinf_campy = c(rep(mid_Pillinf_campy, 7), upper_Pillinf_campy, lower_Pillinf_campy, rep(mid_Pillinf_campy, 2))
    info_organism_campy = c(rep("campy", 11))
    input_percentiles_campy = tibble(rawpathconc_campy, DWvol, LRV_campy, Pillinf_campy, info_organism_campy) %>%
        rename(input_rawpathconc = rawpathconc_campy,
               input_DWvol = DWvol,
               input_LRV = LRV_campy, 
               input_Pillinf = Pillinf_campy,
               info_organism = info_organism_campy)
    
    # Giardia
    rawpathconc_giardia = c(mid_rawpathconc_giardia, upper_rawpathconc_giardia, lower_rawpathconc_giardia, rep(mid_rawpathconc_giardia, 8))
    LRV_giardia = c(rep(mid_LRV_giardia, 5), upper_LRV_giardia, lower_LRV_giardia, rep(mid_LRV_giardia, 4))
    Pillinf_giardia = c(rep(mid_Pillinf_giardia, 7), upper_Pillinf_giardia, lower_Pillinf_giardia, rep(mid_Pillinf_giardia, 2))
    info_organism_giardia = c(rep("giardia", 11))
    input_percentiles_giardia = tibble(rawpathconc_giardia, DWvol, LRV_giardia, Pillinf_giardia, info_organism_giardia) %>%
            rename(input_rawpathconc = rawpathconc_giardia,
                   input_DWvol = DWvol,
                   input_LRV = LRV_giardia, 
                   input_Pillinf = Pillinf_giardia,
                   info_organism = info_organism_giardia)
    
    # Make overall tibble
    input_percentiles = rbind(input_percentiles_campy, input_percentiles_giardia)
    
    # Return tibble
    return(input_percentiles)
    
}

tryinputpercentiles = FUN_inputpercentiles(QMRAdf = allQMRA,
                                          percentile = 0.95)

```



# Make for loop to calculate the deterministic QMRA endpoints for each row in the inputpercentiles dataframe
```{r for loop to calculate deterministic QMRA endpoints}

### Make a for loop to calculate a determinstic QMRA based on the inputs of each row of the inputpercentiles dataframe

# Initialize the QMRA inputs based on the desired percentile
inputpercentiles = FUN_inputpercentiles(QMRAdf = allQMRA,
                                          percentile = 0.95)

### Function to do a for loop that calculates the deterministic QMRA endpoints for each row of the inputpercentiles df

# Inputs:
#  inputpercentiles: df calculated in the function FUN_inputpercentiles, contains point-value inputs for the deterministic QMRA

# Outputs:
#  detQMRA: A df containing the results of all deterministic QMRAs calculated for each row of inputpercentiles

# NOTE: calls the function FUN_detQMRA for each row

FUN_forloop_detQMRA = function(inputpercentiles){


    # Initialize tibble 
    detQMRA = tibble()
    
    
    # For loop here
    for(i in 1:nrow(inputpercentiles)) {
        
        # Check
        print(i)
    
        # Initialize row i
        row <- inputpercentiles[i,]
        
        # Do QMRA
        row_QMRA = FUN_detQMRA(
            rawpathconc = row$input_rawpathconc,
            DWvol = row$input_DWvol,
            LRV = row$input_LRV,
            Pillinf = row$input_Pillinf,
            microbe = row$info_organism
        )
        
        detQMRA = rbind(detQMRA, row_QMRA)
    
    }
    
    return(detQMRA)

}

detQMRA = FUN_forloop_detQMRA(inputpercentiles = inputpercentiles)

```

# A function to get tornado plot data
```{r Function to wrangle data for tornado plot}

### Function to get and wrangle data from the deterministic QMRA for input to a tornado plot

# Inputs:
#  detQMRA: the dataframe of deterministic QMRA endpoints calculated for a specific percentile of inputs, see function FUN_forloop_detQMRA
#  select_organism: string value, should be either "campy" or "giardia"
#  epname: the name of the desired endpoint, should be either "endpoint_exposure", "endpoint_Pinf" or "endpoint_DALY"

# Outputs:
#  tornadodata: dataframe to be passed to the function FUN_maketornadoplot to make the tornado plots



FUN_gettornadodata = function(detQMRA, select_organism, epname){
    
    # Set things to troubleshoot function
    # detQMRA = detQMRA
    # select_organism = "giardia"
    # epname = "endpoint_exposure"
    
    # Subset the QMRAdf 
    detQMRA_select = detQMRA %>%
        filter(info_organism == select_organism)
    
    # Get max/min endpoint values for max/min rawpathconc values
    max_rawpathconc = max(detQMRA_select$input_rawpathconc)
    min_rawpathconc = min(detQMRA_select$input_rawpathconc)
    max_ep_rawpathconc = as.numeric(detQMRA_select[detQMRA_select$input_rawpathconc == max_rawpathconc, epname])
    min_ep_rawpathconc = as.numeric(detQMRA_select[detQMRA_select$input_rawpathconc == min_rawpathconc, epname])
    
    # Get max/min endpoint values for max/min DWvol values
    max_DWvol = max(detQMRA_select$input_DWvol)
    min_DWvol = min(detQMRA_select$input_DWvol)
    max_ep_DWvol = as.numeric(detQMRA_select[detQMRA_select$input_DWvol == max_DWvol, epname])
    min_ep_DWvol = as.numeric(detQMRA_select[detQMRA_select$input_DWvol == min_DWvol, epname])
    
    # Get max/min endpoint values for max/min LRV values
    max_LRV = max(detQMRA_select$input_LRV)
    min_LRV = min(detQMRA_select$input_LRV)
    max_ep_LRV = as.numeric(detQMRA_select[detQMRA_select$input_LRV == max_LRV, epname])
    min_ep_LRV = as.numeric(detQMRA_select[detQMRA_select$input_LRV == min_LRV, epname])
    
    # Get max/min endpoint values for max/min Pillinf values
    max_Pillinf = max(detQMRA_select$input_Pillinf)
    min_Pillinf = min(detQMRA_select$input_Pillinf)
    max_ep_Pillinf = as.numeric(detQMRA_select[detQMRA_select$input_Pillinf == max_Pillinf, epname])
    min_ep_Pillinf = as.numeric(detQMRA_select[detQMRA_select$input_Pillinf == min_Pillinf, epname])
    
    # Get the base case endpoint value for all inputs at 50th percentils
    base_ep = as.numeric(detQMRA_select[1,epname])
    base_ep_col = c(rep(base_ep, 4))
    
    # Wrangle data
    lower_endpoint = c(min_ep_rawpathconc, min_ep_DWvol, min_ep_LRV, min_ep_Pillinf)
    upper_endpoint = c(max_ep_rawpathconc, max_ep_DWvol, max_ep_LRV, min_ep_Pillinf)
    input_name = c("rawpathconc", "DWvol", "LRV", "Pillinf")
    
    # Make tibble
    tornadodata = tibble(lower_endpoint, upper_endpoint, base_ep_col, input_name)

    # Add columns to tornadodata to make plotting easier in the next function
    tornadodata = tornadodata %>%
        # Add column for the difference between upper and lower endpoint values
        mutate(ul_diff = upper_endpoint - lower_endpoint) %>% 
        
        # Add column with the endpoint name for clarity
        mutate(epname = epname) %>%
        
        # Add column with the selected organism for clarity
        mutate(info_organism = select_organism) %>%
        
        # Make column for naming the inputs
        mutate(
            input_name_plot = case_when(
                input_name == "rawpathconc" ~ "Raw pathogen concentration",
                input_name == "DWvol" ~ "Volume of water consumed",
                input_name == "LRV" ~ "Device LRV",
                input_name == "Pillinf" ~ "Probability of illness given infection"
            )
        ) 
        
        
        
    # Delete the row for Pillinf as an input, if the endpoint is exposure or Pinf
    if(epname == "endpoint_exposure" | epname == "endpoint_Pinf"){  
        # Delete the row for Pillinf as an input
        tornadodata = tornadodata %>%
            filter(input_name != "Pillinf")
    } else {
        # Keep Pillinf
        # print("do nothing")
    }
    
    # Return output
    return(tornadodata)
    
}

trytornadodata = FUN_gettornadodata(detQMRA = detQMRA_80, 
                                    select_organism = "campy", 
                                    epname = "endpoint_exposure")

```



# A function to make tornado plot
```{r Function to make tornado plot}

### Function to plot a single tornado plot

# Inputs:
#  tornadodata: data for the tornado plot, from function FUN_gettornadodata

# Outputs:
#  tornadoplot: a ggplot item that is a single tornado plot based on tornadodata



FUN_maketornadoplot = function(tornadodata){
    
    # For troubleshooting
    # tornadodata = trytornadodata
    
    # Define width of columns
    width = 0.95
    
    # Get bar order 
    tornado_order = tornadodata %>%
        arrange(ul_diff) %>%     # Put ascending order by the difference between lower and upper endpoints
        mutate(input_name_plot = factor(x = input_name_plot, levels = input_name_plot)) %>%   # Encode this order into the input_name factor
        dplyr::select(input_name_plot) %>%    # Grab the input_name
        unlist() %>%    # Make it into a vector of chr
        levels()        # This too
    
    
    ## Wrangle dataframe for plotting
    tornadodata_plot = tornadodata %>%
        # Pivot longer so that the endpoint values are all one column
        pivot_longer(               
            cols = ends_with("endpoint"),
            names_to = "endpoint_type",
            values_to = "endpoint_value"
        ) %>%
        
        # Make input_name a factor and order it
        mutate(input_name_plot = factor(input_name_plot, levels = tornado_order)) %>%
        
        # Calculate the coordinates of each rectangle
        mutate(
            ymin = pmin(endpoint_value, base_ep_col),
            ymax = pmax(endpoint_value, base_ep_col), 
            xmin = as.numeric(input_name_plot) - width/2,
            xmax = as.numeric(input_name_plot) + width/2
        ) %>%
        
        # Make column for naming the legend
        mutate(
            endpoint_type_plot = case_when(
                endpoint_type == "lower_endpoint" ~ "Decreased input",
                endpoint_type == "upper_endpoint" ~ "Increased input"
            )
        )
    
    
    
    ## Plot
    
    # Define colours
    brew_2 = c("#A50026", "#4575B4")
    
    # Pull the value for organism name for if/else
    microbe = tornadodata$info_organism[1]
    
    
    # Delete y axis labels if it's a giardia plot, so that when we patchwork it later, they're not repeated
    if(microbe == "campy"){  
        # Campylobacter plots, keep y axis labels
        
        tornadoplot = ggplot() +
            
            # Make main geom
            geom_rect(data = tornadodata_plot, 
                      aes(ymax = ymax, ymin = ymin, 
                          xmin = xmin, xmax = xmax, 
                          fill = endpoint_type_plot)) +
            geom_hline(yintercept = tornadodata_plot$base_ep_col[1]) +
            
            # Order bars in ascending order and set labels
            scale_x_continuous(breaks = c(1:length(tornado_order)),
                               labels = tornado_order) + 
    
            # Make it look nice
            coord_flip() + 
            theme_bw() +
            theme(legend.position = "none",
                  text = element_text(size = 12), 
                  axis.title.y = element_text(size=12),
                  panel.grid.minor = element_blank(), 
                  legend.title= element_blank()) +
            scale_fill_manual(values = brew_2)
        
        
    } else {
        # Giardia plots, delete y axis labels
        
        tornadoplot = ggplot() +
            
            # Make main geom
            geom_rect(data = tornadodata_plot, 
                      aes(ymax = ymax, ymin = ymin, 
                          xmin = xmin, xmax = xmax, 
                          fill = endpoint_type_plot)) +
            geom_hline(yintercept = tornadodata_plot$base_ep_col[1]) +
            
            # Order bars in ascending order
            scale_x_continuous(breaks = c(1:length(tornado_order))) + 
    
            # Make it look nice
            coord_flip() + 
            theme_bw() +
            theme(legend.position = "none",
                  text = element_text(size = 12), 
                  # axis.title.y = element_text(size=12),
                  axis.text.y = element_blank(),
                  panel.grid.minor = element_blank(), 
                  legend.title= element_blank()) +
            scale_fill_manual(values = brew_2)    
        }

    
    # Plot and return
    plot(tornadoplot)
    return(tornadoplot)
    
}

# Make sure the function works
trytornadoplot = FUN_maketornadoplot(tornadodata = trytornadodata)

```


# Put together 6 tornado plots for a given percentile using patchwork
```{r patchwork tornado plots, fig.width= 8, fig.height=11}

### Function to make 6 tornado plots and put them together using patchwork

# Inputs:
#  detQMRA: df with all the results of the deterministic QMRA done using inputs at a given percentile. See function FUN_forloop_detQMRA for how detQMRA is generated

# Outputs: 
#  patch_both: a patchwork/ggplot object that has 6 tornado plots (2 columns of 3, left column for campy and the right for giardia)

# Note: This function also calls the functions FUN_gettornadodata to get the input data for each individual tornado plot, and FUN_maketornadoplot to make ech individual plot



FUN_maketornadopatchwork = function(detQMRA){

    # For troubleshooting
    # detQMRA = detQMRA_80
    
    ### Make the tornado plots 

    ## Campylobacter
    # Campy, exposure
    tornadodata_c_exposure = FUN_gettornadodata(detQMRA = detQMRA, 
                                                   select_organism = "campy", 
                                                   epname = "endpoint_exposure")
    tornadoplot_c_exposure = FUN_maketornadoplot(tornadodata = tornadodata_c_exposure)
    
    # Campy, Pinf
    tornadodata_c_Pinf = FUN_gettornadodata(detQMRA = detQMRA, 
                                                   select_organism = "campy", 
                                                   epname = "endpoint_Pinf")
    tornadoplot_c_Pinf = FUN_maketornadoplot(tornadodata = tornadodata_c_Pinf)
    
    # Campy, DALY
    tornadodata_c_DALY = FUN_gettornadodata(detQMRA = detQMRA, 
                                                   select_organism = "campy", 
                                                   epname = "endpoint_DALY")
    tornadoplot_c_DALY = FUN_maketornadoplot(tornadodata = tornadodata_c_DALY)
    
    
    ## Giardia
    # Giardia, exposure
    tornadodata_g_exposure = FUN_gettornadodata(detQMRA = detQMRA, 
                                                   select_organism = "giardia", 
                                                   epname = "endpoint_exposure")
    tornadoplot_g_exposure = FUN_maketornadoplot(tornadodata = tornadodata_g_exposure)
    
    # Giardia, Pinf
    tornadodata_g_Pinf = FUN_gettornadodata(detQMRA = detQMRA, 
                                                   select_organism = "giardia", 
                                                   epname = "endpoint_Pinf")
    tornadoplot_g_Pinf = FUN_maketornadoplot(tornadodata = tornadodata_g_Pinf)
    
    # Giardia, DALY
    tornadodata_g_DALY = FUN_gettornadodata(detQMRA = detQMRA, 
                                                   select_organism = "giardia", 
                                                   epname = "endpoint_DALY")
    tornadoplot_g_DALY = FUN_maketornadoplot(tornadodata = tornadodata_g_DALY)
    
    
    ## Patchwork them together
    patch_both = (tornadoplot_c_exposure + tornadoplot_g_exposure) /
                 (tornadoplot_c_Pinf + tornadoplot_g_Pinf) /
                 (tornadoplot_c_DALY + tornadoplot_g_DALY) 
                 
    plot(patch_both)
    return(patch_both)

}

# Try the function
patch_both_try = FUN_maketornadopatchwork(detQMRA = detQMRA) 

```


# Make tornado plots, 20th to 80th percentiles
```{r tornado plots for 20th to 80th percentiles, fig.width= 8, fig.height=11}

### Step 1: Pull percentile information from QMRA
inputpercentiles_80 = FUN_inputpercentiles(QMRAdf = allQMRA,
                                          percentile = 0.8)

### Step 2: Calculate a deterministic QMRA for each row of inputpercentiles
detQMRA_80 = FUN_forloop_detQMRA(inputpercentiles = inputpercentiles_80)
# Change one value of the giardia LRVs to 2.99999 (instead of 3) because the 20th percentile LRV is the same as the median
detQMRA_80$input_LRV[18] = 2.999


### Step 3: Make tornado plots
patch_both_80 = FUN_maketornadopatchwork(detQMRA = detQMRA_80) +
                    plot_annotation(
                           title = paste("Endpoints resulting from QMRA inputs",
                                         "held at the 20th and 80th percentiles",
                                          sep = "\n")) +
                    theme(plot.title = element_text(size = 14, hjust = 0))    # Left-aligned
plot(patch_both_80)


# Save figure for publication
ggsave("output_QMRA/tornado_80.png", 
        plot = patch_both_80,
        dpi = 300,
        width = 8.5,
        height = 11,
        units = "in")

```



# Make tornado plots, 10th to 90th percentiles
```{r tornado plots for 10th to 90th percentiles, fig.width= 8, fig.height=11}

### Step 1: Pull percentile information from QMRA
inputpercentiles_90 = FUN_inputpercentiles(QMRAdf = allQMRA,
                                          percentile = 0.9)

### Step 2: Calculate a deterministic QMRA for each row of inputpercentiles
detQMRA_90 = FUN_forloop_detQMRA(inputpercentiles = inputpercentiles_90)

### Step 3: Make tornado plots
patch_both_90 = FUN_maketornadopatchwork(detQMRA = detQMRA_90) +
                    plot_annotation(
                           title = paste("Endpoints resulting from QMRA inputs",
                                         "held at the 10th and 90th percentiles",
                                          sep = "\n")) +
                    theme(plot.title = element_text(size = 14, hjust = 0))    # Left-aligned
plot(patch_both_90)


# Save figure for publication
ggsave("output_QMRA/tornado_90.png", 
        plot = patch_both_90,
        dpi = 300,
        width = 8.5,
        height = 11,
        units = "in")

```


# Make tornado plots, 1st to 99th percentiles
```{r tornado plots for 1st to 99th percentiles, fig.width= 8, fig.height=11}

### Step 1: Pull percentile information from QMRA
inputpercentiles_99 = FUN_inputpercentiles(QMRAdf = allQMRA,
                                          percentile = 0.99)

### Step 2: Calculate a deterministic QMRA for each row of inputpercentiles
detQMRA_99 = FUN_forloop_detQMRA(inputpercentiles = inputpercentiles_99)

### Step 3: Make tornado plots
patch_both_99 = FUN_maketornadopatchwork(detQMRA = detQMRA_99) +
                    plot_annotation(
                           title = paste("Endpoints resulting from QMRA inputs",
                                         "held at the 1st and 99th percentiles",
                                          sep = "\n")) +
                    theme(plot.title = element_text(size = 14, hjust = 0))    # Left-aligned
plot(patch_both_99)


# Save figure for publication
ggsave("output_QMRA/tornado_99.png", 
        plot = patch_both_99,
        dpi = 300,
        width = 8.5,
        height = 11,
        units = "in")

```



# Try an example tornado plot from the internet
```{r try tornado from internet}



# # https://rdrr.io/cran/mc2d/man/ggtornado.html
# data(ec)
# x <- evalmcmod(ec$modEC2, nsv=100, nsu=100, seed=666)
# tor <- tornado(x, 7)
# ggtornado(tor)
# data(total)
# ggtornado(tornadounc(total, 10, use="complete.obs"), which=1)


# https://stackoverflow.com/questions/55751978/tornado-both-sided-horizontal-bar-plot-in-r-with-chart-axes-crosses-at-a-given

library(ggplot2)
library(plyr)
library(dplyr)
library(tidyverse)

df <- '
Parameter Lower_Bound Upper_Bound UL_Difference
Parameter01 8074 11181 3108 
Parameter02 8177 11007 2831 
Parameter03 8879 10188 1308 
Parameter04 4358 18697 14339 
Parameter05 9073 10087 1013 
Parameter06 12034 7572 4462 
Parameter07 11357 7933 3423 
Parameter08 9769 9202 567 
Parameter09 8833 10403 1570 
Parameter10 13450 4219 9231 
Parameter11 10691 7915 2776 
Parameter12 10036 8792 1244
' %>% read_table2()

# original value of output
base.value <- 9504

# get order of parameters according to size of intervals
# (I use this to define the ordering of the factors which I then use to define the positions in the plot)
order.parameters <- df %>% arrange(UL_Difference) %>%
  mutate(Parameter=factor(x=Parameter, levels=Parameter)) %>%
  dplyr::select(Parameter) %>% unlist() %>% levels()

# width of columns in plot (value between 0 and 1)
width <- 0.95

# get data frame in shape for ggplot and geom_rect
df.2 <- df %>% 
  # gather columns Lower_Bound and Upper_Bound into a single column using gather
  gather(key='type', value='output.value', Lower_Bound:Upper_Bound) %>%
  # just reordering columns
  dplyr::select(Parameter, type, output.value, UL_Difference) %>%
  # create the columns for geom_rect
  mutate(Parameter=factor(Parameter, levels=order.parameters),
         ymin=pmin(output.value, base.value),
         ymax=pmax(output.value, base.value),
         xmin=as.numeric(Parameter)-width/2,
         xmax=as.numeric(Parameter)+width/2)

# create plot
# (use scale_x_continuous to change labels in y axis to name of parameters)
ggplot() + 
  geom_rect(data = df.2, 
            aes(ymax=ymax, ymin=ymin, xmax=xmax, xmin=xmin, fill=type)) +
  theme_bw() + 
  theme(axis.title.y=element_blank(), legend.position = 'bottom',
        legend.title = element_blank()) + 
  geom_hline(yintercept = base.value) +
  scale_x_continuous(breaks = c(1:length(order.parameters)), 
                     labels = order.parameters) +
  coord_flip()


```


